\begin{glossarymc}[Cambridge 14]
    \begin{test}{TEST 1}
    \noindent
    \textbf{Part 1. Future}
    \begin{qa}{What job would you like to have ten years from now? [Why?]}
    Since I graduated from university, I haven’t changed my job yet. \textbf{My heart was set on} becoming a teacher when I was little and luckily, I managed to \textbf{fulfill} this dream upon graduation. This job is also steady so I \textbf{don’t have the slightest idea about} switching to other professions. \textbf{There is a likelihood} that I will \textbf{stick to} this job till the end of my life. I don’t see myself \textbf{packing in} this job in the near future.
    \end{qa}

    \begin{qa}{How useful will English be for your future? [Why/Why not?]}
    As an English teacher myself, it is a \textbf{prerequisite for} having a good command of English to teach my students effectively. I also need to develop my English proficiency to meet the increasing demands of both parents and students in the future.
    \end{qa}

    \begin{qa}{How much travelling do you hope to do in the future? [Why/Why not?]}
    As I have visited 14 countries \textbf{under my belt}, I still \textbf{long for} the 15th, 16th and so on. In fact, I have not been to the USA yet so I’d like to \textbf{set foot in} this country one day.
    \end{qa}

    \begin{qa}{How do you think your life will change in the future? [Why/Why not?]}
    I don’t think there will be too many changes to my life as long as I still \textbf{keep a low profile} like this. The biggest yet anticipated change might be brought about by the birth of my second child. My daughter needs a sibling to play with, I guess.
    \end{qa}

        \begin{VocabExplain}[Part 1]
            \begin{ExplainCard}{my heart was set on}[idiom][C1]
            \EN{To be determined or strongly desire to do or achieve something.}
            \SY{determined on; focused on}
            \VI{quyết tâm, khao khát làm gì.}
            \EX{My heart was set on becoming a doctor.}
            \EX{Her heart is set on studying abroad.}
            \CO{heart set on sth}
            \end{ExplainCard}

            \begin{ExplainCard}{fulfill}[v][B2]
            \EN{To achieve or realize something desired or promised.}
            \SY{achieve; carry out; accomplish}
            \VI{hoàn thành, thực hiện.}
            \EX{She fulfilled her childhood dream of becoming a singer.}
            \EX{The company fulfilled its promise to improve safety.}
            \CO{fulfill a dream; fulfill a requirement}
            \end{ExplainCard}

            \begin{ExplainCard}{don’t have the slightest idea about}[idiom][B2]
            \EN{To have absolutely no knowledge or understanding of something.}
            \SY{no clue; no idea}
            \VI{không hề biết, hoàn toàn không hiểu.}
            \EX{I don’t have the slightest idea about cars.}
            \EX{He didn’t have the slightest idea about what happened.}
            \CO{don’t have the slightest idea about sth}
            \end{ExplainCard}

            \begin{ExplainCard}{there is a likelihood}[phrase][C1]
            \EN{There is a strong chance or probability that something will happen.}
            \SY{possibility; probability; chance}
            \VI{có khả năng.}
            \EX{There is a likelihood of rain this afternoon.}
            \EX{There is a likelihood that he will be promoted.}
            \CO{there is a likelihood that + clause}
            \end{ExplainCard}

            \begin{ExplainCard}{stick to}[phr.v][B2]
            \EN{To continue doing something without changing it.}
            \SY{persist in; adhere to; remain with}
            \VI{gắn bó, kiên trì với.}
            \EX{Stick to your plan and you’ll succeed.}
            \EX{He sticks to his principles no matter what.}
            \CO{stick to the rules; stick to a job}
            \end{ExplainCard}

            \begin{ExplainCard}{pack in}[phr.v][C1]
            \EN{To stop doing something, especially a job or habit.}
            \SY{quit; give up; abandon}
            \VI{bỏ, nghỉ.}
            \EX{She decided to pack in her boring job.}
            \EX{He packed in smoking after 10 years.}
            \CO{pack in a job; pack in a habit}
            \end{ExplainCard}

            \begin{ExplainCard}{prerequisite for}[phrase][C1]
            \EN{Something that is required as a condition for something else.}
            \SY{requirement; condition; necessity}
            \VI{điều kiện tiên quyết.}
            \EX{Passing the test is a prerequisite for graduation.}
            \EX{Fluency in English is a prerequisite for this position.}
            \CO{prerequisite for sth}
            \end{ExplainCard}

            \begin{ExplainCard}{under my belt}[idiom][C1]
            \EN{Having achieved or experienced something.}
            \SY{achieved; accomplished}
            \VI{có được, tích lũy được (kinh nghiệm, thành tựu).}
            \EX{He already has several victories under his belt.}
            \EX{She has years of experience under her belt.}
            \CO{under sb’s belt}
            \end{ExplainCard}

            \begin{ExplainCard}{long for}[phr.v][B2]
            \EN{To have a strong desire for something.}
            \SY{yearn for; crave; desire}
            \VI{khao khát, mong mỏi.}
            \EX{I long for a holiday by the sea.}
            \EX{She longed for her family during the trip.}
            \CO{long for sth}
            \end{ExplainCard}

            \begin{ExplainCard}{set foot in}[idiom][B2]
            \EN{To go into a place, especially for the first time.}
            \SY{enter; go into}
            \VI{đặt chân đến.}
            \EX{He has never set foot in Paris.}
            \EX{She set foot in the museum last summer.}
            \CO{set foot in a country/place}
            \end{ExplainCard}

            \begin{ExplainCard}{keep a low profile}[idiom][C1]
            \EN{To avoid attracting attention or publicity.}
            \SY{stay unnoticed; remain inconspicuous}
            \VI{giữ kín tiếng, tránh gây chú ý.}
            \EX{He decided to keep a low profile after the scandal.}
            \EX{She prefers to keep a low profile at work.}
            \CO{keep a low profile; maintain a low profile}
            \end{ExplainCard}
        \end{VocabExplain}

    \noindent
    \textbf{Part 2.}
    \begin{qa}{Describe a book that you enjoy reading because you had to think a lot. You should say:
    \begin{itemize}
        \item What this book was
        \item Why you decided to read it
        \item What reading this book made you think about
        \item and explain why you enjoyed reading this book
    \end{itemize}}

    To be honest, I am not a \textbf{bookworm}, but sometimes reading books is \textbf{an escape for me}. If you ask me what book I \textbf{get a kick out of} reading, I would probably describe the book titled: Financial Management. This book changed my former concept of saving money. This book was written by Vu Thang Trung, who is a senior financial consultant in a multinational company. 

    Talking about the reasons why I decided to read it, it was due to the fact that I was always \textbf{short of money} although I had a decent job. Some of my friends did not have high salary like me, but they had financial security. So I thought this book enabled me to have a deeper understanding of financial management. Unlike many books, this book asked readers many questions so that they could \textbf{take their habits into account}. 

    After spending two hours \textbf{delving into} this book, I \textbf{came to the conclusion} that I did not know which items should be \textbf{prioritized}, so sometimes I spent money lavishly and eventually, my accounts were sometimes \textbf{in the red} after a \textbf{spending spree}. Concerning why I was absorbed in reading this book, I guess the main reason is that it helped to \textbf{get to the bottom of} my financial problems and offered some effective suggestions. 

    First, it would be better if I deposited my idle cash into the bank to receive a bigger sum upon the expiry of my bank account. Second, I was advised to make cash transactions regularly in lieu of credit cards, which might allow me to stay out of debt later on. Accordingly, I still \textbf{take heed of} his advice for the time being and things are \textbf{looking up}. Thanks to his book, I did not \textbf{rack up a debt} any more.
    \end{qa}

        \begin{VocabExplain}[Part 2]
            \begin{ExplainCard}{bookworm}[n][C1]
            \EN{A person who enjoys reading very much.}
            \SY{avid reader; bibliophile}
            \VI{mọt sách, người ham đọc sách.}
            \EX{She’s a real bookworm who spends all her time in the library.}
            \EX{Bookworms often have extensive vocabularies.}
            \CO{be a bookworm}
            \end{ExplainCard}

            \begin{ExplainCard}{an escape}[n][B2]
            \EN{Something that provides relief or distraction from reality.}
            \SY{distraction; relief; break}
            \VI{lối thoát, cách giải tỏa.}
            \EX{Reading is an escape from stress for me.}
            \EX{Music became his escape from daily struggles.}
            \CO{an escape from sth}
            \end{ExplainCard}

            \begin{ExplainCard}{get a kick out of}[idiom][C1]
            \EN{To greatly enjoy something.}
            \SY{enjoy; relish; take pleasure in}
            \VI{thích thú với điều gì.}
            \EX{He gets a kick out of playing football.}
            \EX{I got a kick out of watching that comedy.}
            \CO{get a kick out of sth}
            \end{ExplainCard}

            \begin{ExplainCard}{short of money}[phrase][B2]
            \EN{Not having enough money.}
            \SY{broke; poor; strapped for cash}
            \VI{thiếu tiền.}
            \EX{I can’t go out this week, I’m short of money.}
            \EX{Many students are always short of money.}
            \CO{be short of money}
            \end{ExplainCard}

            \begin{ExplainCard}{take into account}[phrase][B2]
            \EN{To consider something when making a decision.}
            \SY{consider; regard; factor in}
            \VI{xem xét, tính đến.}
            \EX{We must take his age into account.}
            \EX{They took the new law into account when planning.}
            \CO{take sth into account}
            \end{ExplainCard}

            \begin{ExplainCard}{delve into}[phr.v][C1]
            \EN{To investigate or research deeply.}
            \SY{explore; investigate; examine}
            \VI{đào sâu vào, nghiên cứu kỹ.}
            \EX{She delved into the history of the family.}
            \EX{The article delves into the causes of poverty.}
            \CO{delve into details; delve into issues}
            \end{ExplainCard}

            \begin{ExplainCard}{come to the conclusion}[phrase][B2]
            \EN{To decide after considering all the information.}
            \SY{decide; determine; infer}
            \VI{đi đến kết luận.}
            \EX{I came to the conclusion that he was right.}
            \EX{They came to the conclusion after hours of debate.}
            \CO{come to the conclusion that + clause}
            \end{ExplainCard}

            \begin{ExplainCard}{prioritize}[v][C1]
            \EN{To decide what tasks are most important and do them first.}
            \SY{rank; arrange; emphasize}
            \VI{ưu tiên.}
            \EX{You must prioritize tasks when busy.}
            \EX{The company prioritizes customer satisfaction.}
            \CO{prioritize work; prioritize needs}
            \end{ExplainCard}

            \begin{ExplainCard}{in the red}[idiom][C1]
            \EN{Owing money; in debt.}
            \SY{in debt; insolvent}
            \VI{thua lỗ, mắc nợ.}
            \EX{The company has been in the red for years.}
            \EX{I was in the red after overspending.}
            \CO{be in the red}
            \end{ExplainCard}

            \begin{ExplainCard}{spending spree}[n][C1]
            \EN{A short period of extravagant spending.}
            \SY{splurge; extravagance}
            \VI{mua sắm bừa bãi, tiêu xài hoang phí.}
            \EX{She went on a spending spree with her bonus.}
            \EX{A spending spree can ruin your finances.}
            \CO{go on a spending spree}
            \end{ExplainCard}

            \begin{ExplainCard}{get to the bottom of}[idiom][C1]
            \EN{To discover the real cause of something.}
            \SY{investigate; uncover; understand}
            \VI{hiểu rõ ngọn ngành.}
            \EX{The manager got to the bottom of the problem.}
            \EX{We need to get to the bottom of this issue.}
            \CO{get to the bottom of sth}
            \end{ExplainCard}

            \begin{ExplainCard}{take heed of}[phrase][C1]
            \EN{To pay attention to and consider seriously.}
            \SY{heed; follow; observe}
            \VI{chú ý đến, nghe theo.}
            \EX{He took heed of the doctor’s advice.}
            \EX{You must take heed of the warning signs.}
            \CO{take heed of sth}
            \end{ExplainCard}

            \begin{ExplainCard}{looking up}[idiom][B2]
            \EN{Improving or getting better.}
            \SY{improving; brightening; progressing}
            \VI{khởi sắc, tiến triển tốt.}
            \EX{Things are looking up for the economy.}
            \EX{Business is finally looking up.}
            \CO{things are looking up}
            \end{ExplainCard}

            \begin{ExplainCard}{rack up a debt}[idiom][C1]
            \EN{To accumulate a large amount of debt.}
            \SY{incur; amass; accumulate}
            \VI{tích lũy nợ nần.}
            \EX{He racked up a debt after years of gambling.}
            \EX{Students often rack up debt during college.}
            \CO{rack up a debt; rack up losses}
            \end{ExplainCard}
        \end{VocabExplain}

    \noindent
    \textbf{Part 3.}
    \begin{qa}{What are the most popular types of children’s books in your country?}
    From my experience, rhyme collections, detective stories and fairy tales are \textbf{well-liked} by children in my country. However, the preference is divided according to gender and \textbf{temperament}. A large number of girls are \textbf{die-hard} fans of fairy tales because of nice illustration and romantic adventures while the majority of boys would pick detective stories in order to satisfy their curiosity when a case is closed.
    \end{qa}

    \begin{qa}{What are the benefits of parents reading books to their children?}
    There have been many studies that show reading to babies and toddlers gives them \textbf{a head start} and helps to prepare them for school \textbf{later down the line}. In fact, reading together encourages a \textbf{thirst for knowledge}, which provides both parents and their children a chance to speak about what is happening and use this as a learning experience.
    \end{qa}

    \begin{qa}{Should parents always let children choose the books they read?}
    To some extent, parents should give their children greater \textbf{autonomy} in their life, by allowing them to choose their favorite books, for example. Still, this does not always work as kids choose a book because they are into the nicely illustrated cover, although the content is not actually a match for their interests or reading level. Moreover, age labelling is another problem that \textbf{deters} children from choosing their books, therefore, parents should take an active role in helping their children to pick up suitable books.
    \end{qa}

    \begin{qa}{How popular are electronic books in your country?}
    The popularity of e-textbooks is increasing at an \textbf{unprecedented} rate. This is particularly true for young people these days who drive their \textbf{appetite} for the type of book. Unlike printed books, ebooks can be downloaded or bought online, which can create a feeling of \textbf{gratification} to the customers. Till now, electronic books have become integral to people in my country.
    \end{qa}

    \begin{qa}{What are the advantages of parents reading electronic books (compared to printed books)?}
    Honestly, I used to be among those paper book \textbf{fundamentalists} that did not favor electronic books. Now, I would say that I \textbf{dedicate} parts of my interest to ebooks for some reason. Firstly, \textbf{portability} is a major advantage for readers who want to take the book everywhere. Secondly, no trees are required to manufacture paper for the pages of ebooks, which may protect the forests and prevent natural \textbf{depletion} as well.
    \end{qa}

    \begin{qa}{Will electronic books ever completely replace printed books in the future?}
    In my opinion, printed books cannot \textbf{vanish} as long as people still want to buy them. Basically, reading printed books is \textbf{instrumental} in getting a sound sleep as it has been discovered that the blue lights from tablets or phones \textbf{hampers} the ability of a person to sleep. Furthermore, digital reading involves the active usage of the Internet. Hence, this can interrupt the proper reading process whereas no one gets disturbed with printed books as they do not get any notifications popping up out of nowhere from apps like Facebook or Messenger.
    \end{qa}

        \begin{VocabExplain}[Part 3]
            \begin{ExplainCard}{well-liked}[adj][B2]
            \EN{Liked by many people; popular.}
            \SY{popular; admired; favored}
            \VI{được yêu thích, ưa chuộng.}
            \EX{He is well-liked by his classmates.}
            \EX{This well-liked book has been translated into 20 languages.}
            \CO{well-liked teacher; well-liked brand}
            \end{ExplainCard}

            \begin{ExplainCard}{temperament}[n][C1]
            \EN{A person’s nature that affects their behavior.}
            \SY{character; personality; disposition}
            \VI{tính khí, khí chất.}
            \EX{She has an artistic temperament.}
            \EX{Temperament influences how people react to stress.}
            \CO{artistic temperament; fiery temperament}
            \end{ExplainCard}

            \begin{ExplainCard}{die-hard}[adj][C1]
            \EN{Strongly opposing change and refusing to give up.}
            \SY{stubborn; unyielding; dedicated}
            \VI{cuồng nhiệt, trung thành.}
            \EX{He is a die-hard fan of the team.}
            \EX{Die-hard supporters refused to leave.}
            \CO{die-hard fan; die-hard supporter}
            \end{ExplainCard}

            \begin{ExplainCard}{a head start}[idiom][C1]
            \EN{An advantage that makes success easier or more likely.}
            \SY{advantage; early start}
            \VI{lợi thế ban đầu.}
            \EX{Her training gave her a head start in the competition.}
            \EX{Children who read early have a head start in school.}
            \CO{give sb a head start; get a head start}
            \end{ExplainCard}

            \begin{ExplainCard}{later down the line}[idiom][C1]
            \EN{At some point in the future.}
            \SY{in the future; eventually}
            \VI{trong tương lai sau này.}
            \EX{We may face problems later down the line.}
            \EX{He might change his career later down the line.}
            \CO{later down the line}
            \end{ExplainCard}

            \begin{ExplainCard}{thirst for knowledge}[phrase][C1]
            \EN{A strong desire to learn.}
            \SY{curiosity; eagerness}
            \VI{khao khát học hỏi.}
            \EX{He showed a thirst for knowledge from a young age.}
            \EX{Reading feeds our thirst for knowledge.}
            \CO{thirst for knowledge}
            \end{ExplainCard}

            \begin{ExplainCard}{autonomy}[n][C1]
            \EN{The ability to make independent decisions.}
            \SY{independence; self-government}
            \VI{tự chủ, tự quyết.}
            \EX{Students should be given more autonomy.}
            \EX{Autonomy at work improves motivation.}
            \CO{grant autonomy; individual autonomy}
            \end{ExplainCard}

            \begin{ExplainCard}{deter}[v][C1]
            \EN{To discourage someone from doing something.}
            \SY{discourage; prevent}
            \VI{ngăn cản, làm nản lòng.}
            \EX{High prices deter customers from buying.}
            \EX{Strict laws deter people from crimes.}
            \CO{deter sb from doing sth}
            \end{ExplainCard}

            \begin{ExplainCard}{unprecedented}[adj][C1]
            \EN{Never having happened before.}
            \SY{extraordinary; unmatched; unheard-of}
            \VI{chưa từng có tiền lệ.}
            \EX{The company had unprecedented success.}
            \EX{This is an unprecedented opportunity.}
            \CO{unprecedented growth; unprecedented event}
            \end{ExplainCard}

            \begin{ExplainCard}{appetite}[n][C1]
            \EN{A strong desire for something.}
            \SY{desire; craving; urge}
            \VI{sự thèm muốn, khao khát.}
            \EX{She has an appetite for adventure.}
            \EX{There’s a growing appetite for online learning.}
            \CO{appetite for sth}
            \end{ExplainCard}

            \begin{ExplainCard}{gratification}[n][C1]
            \EN{Pleasure or satisfaction gained from something.}
            \SY{satisfaction; fulfillment}
            \VI{sự thỏa mãn.}
            \EX{Helping others gave her great gratification.}
            \EX{The gratification of winning was enormous.}
            \CO{instant gratification; seek gratification}
            \end{ExplainCard}

            \begin{ExplainCard}{fundamentalist}[n][C1]
            \EN{A person who strictly follows a set of beliefs.}
            \SY{traditionalist; purist}
            \VI{người bảo thủ, người theo chủ nghĩa cơ bản.}
            \EX{He is a fundamentalist in education.}
            \EX{Religious fundamentalists oppose reforms.}
            \CO{religious fundamentalist; strict fundamentalist}
            \end{ExplainCard}

            \begin{ExplainCard}{dedicate}[v][B2]
            \EN{To give time or effort to something.}
            \SY{devote; commit}
            \VI{cống hiến, dành cho.}
            \EX{She dedicates her life to teaching.}
            \EX{He dedicated hours to his project.}
            \CO{dedicate time; dedicate oneself to}
            \end{ExplainCard}

            \begin{ExplainCard}{portability}[n][C1]
            \EN{The ability to be easily carried or moved.}
            \SY{mobility; transportability}
            \VI{tính di động.}
            \EX{Laptops offer great portability.}
            \EX{Portability is a key feature of smartphones.}
            \CO{high portability; portability of devices}
            \end{ExplainCard}

            \begin{ExplainCard}{depletion}[n][C1]
            \EN{The reduction in the number or quality of something.}
            \SY{exhaustion; reduction}
            \VI{sự cạn kiệt.}
            \EX{Oil depletion is a global concern.}
            \EX{Depletion of resources threatens the planet.}
            \CO{resource depletion; depletion of forests}
            \end{ExplainCard}

            \begin{ExplainCard}{vanish}[v][B2]
            \EN{To disappear suddenly or completely.}
            \SY{disappear; fade; evaporate}
            \VI{biến mất.}
            \EX{The magician vanished from the stage.}
            \EX{All hopes vanished after the failure.}
            \CO{vanish into thin air}
            \end{ExplainCard}

            \begin{ExplainCard}{instrumental}[adj][C1]
            \EN{Essential in causing something to happen.}
            \SY{crucial; key; significant}
            \VI{đóng vai trò quan trọng.}
            \EX{She was instrumental in the project’s success.}
            \EX{Good teachers are instrumental to students’ growth.}
            \CO{instrumental in sth}
            \end{ExplainCard}

            \begin{ExplainCard}{hamper}[v][C1]
            \EN{To make it difficult for something to happen.}
            \SY{hinder; obstruct; impede}
            \VI{cản trở.}
            \EX{The rain hampered the construction work.}
            \EX{Strict rules hamper innovation.}
            \CO{hamper progress; hamper efforts}
            \end{ExplainCard}
        \end{VocabExplain}

    \begin{VocabHighlights}
        \VH{my heart was set on V-ing}{(idiom) be determined to V-inf}{(thành ngữ) quyết tâm trở thành}
        \VH{I don’t have the slightest idea about}{(phrase) I don’t know anything about}{(cụm từ) tôi không biết gì về}
        \VH{There’s a likelihood that}{(phrase) There’s probability that}{(cụm từ) có khả năng là}
        \VH{to stick to}{(v) adhere to a commitment, belief, or rule; continue or confine oneself to doing something}{(động từ) gắn bó với}
        \VH{to pack in}{(phrasal verb) to give up}{(cụm động từ) từ bỏ}
        \VH{I don’t see myself V-ing}{(phrase) I don’t think I will V-inf}{(cụm từ) tôi không nghĩ mình sẽ}
        \VH{a prerequisite for}{(n) something that must exist or happen before something else can happen or be done}{(danh từ) điều kiện tiên quyết}
        \VH{under one’s belt}{(idiom) to have already achieved or obtained something}{(thành ngữ) đạt được điều gì}
        \VH{to long for}{(v) to want something very much, especially if it does not seem likely to happen soon}{(động từ) khao khát cái gì}
        \VH{to set foot in/on}{(idiom) to enter; go into}{(thành ngữ) đặt chân lên}
        \VH{to keep a low profile}{(idiom) to avoid attraction}{(thành ngữ) tránh sự chú ý}
        \VH{a bookworm}{(n) a person who likes reading very much}{(danh từ) con mọt sách}
        \VH{to get a kick out of}{(phrase) to have pleasure from}{(cụm từ) có niềm vui từ}
        \VH{short of money}{(phrase) to lack money}{(cụm từ) thiếu tiền}
        \VH{to have profound insight into}{(phrase) to have a deep understanding of}{(cụm từ) có kiến thức chuyên sâu}
        \VH{to delve into}{(phrase) to dig deeper into something}{(cụm từ) đào sâu}
        \VH{to take something into account}{(phrase) to consider}{(cụm từ) xem xét}
        \VH{in the red}{(idiom) lack money}{(thành ngữ) thiếu tiền}
        \VH{a spending spree}{(phrase) a series of high-value purchases made in a short time}{(cụm từ) sự tiêu xài hoang phí}
        \VH{to be absorbed in}{(phrase) be interested in}{(cụm từ) say mê, chìm đắm}
        \VH{to get to the bottom of}{(idiom) to solve a problem}{(thành ngữ) giải quyết vấn đề}
        \VH{to take heed of}{(idiom) to attend to something}{(thành ngữ) chú ý cái gì đó}
        \VH{to look up}{(phrase) to become brighter}{(cụm từ) trở nên tươi sáng hơn}
        \VH{to rack up a debt}{(phrase) to get into debt}{(cụm từ) vướng vào nợ nần}
        \VH{well-liked}{(adj) liked by many people}{(tính từ) được ưa chuộng}
        \VH{temperament}{(n) a person's or an animal's nature as shown in behavior or reactions}{(danh từ) tính cách}
        \VH{die-hard}{(adj) a belief or behavior that takes a long time to disappear}{(tính từ) cố hữu, từ rất lâu}
        \VH{toddlers}{(n) a young child learning to walk}{(danh từ) trẻ chập chững tập đi}
        \VH{a head start}{(n) an advantage before starting something}{(danh từ) khởi đầu tốt đẹp}
        \VH{down the line}{(idiom) at a later or future point}{(thành ngữ) trong tương lai}
        \VH{a thirst for knowledge}{(phrase) strong desire to learn}{(cụm từ) khát khao kiến thức}
        \VH{autonomy}{(n) ability to act independently}{(danh từ) quyền tự quyết}
        \VH{to deter}{(v) to discourage someone from doing something}{(động từ) răn đe, ngăn cản}
        \VH{unprecedented}{(adj) never happened before}{(tính từ) chưa từng xảy ra}
        \VH{appetite}{(n) physical desire for food}{(danh từ) sự thèm ăn}
        \VH{gratification}{(n) pleasure or satisfaction}{(danh từ) sự hài lòng}
        \VH{fundamentalists}{(n) a person who follows very strictly the basic rules and teachings of a religion}{(danh từ) người theo chủ nghĩa truyền thống}
        \VH{to dedicate}{(v) to give a lot of your time and effort to a particular activity or purpose because you think it is important}{(động từ) cống hiến}
        \VH{portability}{(n) the quality of being easy to carry or to move}{(danh từ) tính di động}
        \VH{depletion}{(n) a reduction in something}{(danh từ) sự suy giảm}
        \VH{to vanish}{(v) to disappear suddenly and/or in a way that you cannot explain}{(động từ) biến mất}
        \VH{to be instrumental in}{(adj) important in making something happen}{(tính từ) đóng vai trò quan trọng}
        \VH{to hamper}{(v) to prevent someone doing something easily}{(động từ) ngăn cản, cản trở}
    \end{VocabHighlights}
    \end{test}

    \begin{test}{TEST 2}
    \noindent
    \textbf{Part 1. Social media}
    \begin{qa}{Which social media websites do you use?}
    Although I set up an account on Twitter, I rarely use it. Facebook is the social networking site I devote most of my time to thanks to a huge number of friends on it. A minority of my friends have Twitter accounts whereas a majority possess at least a Facebook account. The \textbf{onslaught} of these platforms has become a \textbf{de facto} means of communication these days.
    \end{qa}

    \begin{qa}{How much time do you spend on social media sites? [Why/Why not?]}
    Maybe two or three hours a day. I surf Facebook not only to communicate with my friends but I also need to \textbf{stay tuned to} whatever is happening around me. I also take advantage of Facebook to order online items as I can easily chat and bargain with shop assistants \textbf{in the blink of an eye}.
    \end{qa}

    \begin{qa}{What kind of information about yourself have you put on social media? [Why/Why not?]}
    I’ve posted some basic facts about me including my education background, marital status, life events and so on to make a brief introduction about myself. I believe what I’ve shared until now is neither sensitive nor \textbf{calling others’ names}. These things are \textbf{innocuous} and there’s no need to take them down for any reasons.
    \end{qa}

    \begin{qa}{Is there anything you don’t like about social media? [Why?]}
    One thing I feel \textbf{displeased with} social networks is cyber bullying. Once false, misleading or unbiased information is \textbf{sensationalized} and conveyed, it might \textbf{spread like wildfire} without users’ bothering to check its source. If it is aimed at someone, he or she may become \textbf{victimized} for what they \textbf{do not have the faintest idea about}. The victim may be faced with a \textbf{barrage} of criticisms from the public and \textbf{driven to despair}.
    \end{qa}

        \begin{VocabExplain}[Part 1]
            \begin{ExplainCard}{onslaught}[n][C1]
            \EN{A very powerful attack or strong criticism.}
            \SY{attack; assault; offensive}
            \VI{cuộc tấn công, sự công kích dữ dội.}
            \EX{The city struggled to survive the onslaught of invaders.}
            \EX{The politician faced an onslaught of media questions.}
            \CO{onslaught of criticism; military onslaught}
            \end{ExplainCard}

            \begin{ExplainCard}{de facto}[adj/adv][C1]
            \EN{Existing in reality or fact, even if not officially recognized.}
            \SY{in practice; actual; real}
            \VI{trên thực tế, thực sự.}
            \EX{He became the de facto leader of the group.}
            \EX{The city is de facto independent.}
            \CO{de facto standard; de facto authority}
            \end{ExplainCard}

            \begin{ExplainCard}{stay tuned to}[idiom][B2]
            \EN{To keep paying attention to something in order to be informed.}
            \SY{keep updated; follow; monitor}
            \VI{theo dõi sát, cập nhật liên tục.}
            \EX{Stay tuned to the news for further details.}
            \EX{She stayed tuned to the latest fashion trends.}
            \CO{stay tuned to sth}
            \end{ExplainCard}

            \begin{ExplainCard}{in the blink of an eye}[idiom][B2]
            \EN{Very quickly, in an instant.}
            \SY{instantly; immediately; suddenly}
            \VI{chỉ trong nháy mắt.}
            \EX{The accident happened in the blink of an eye.}
            \EX{The technology spreads in the blink of an eye.}
            \CO{happen in the blink of an eye}
            \end{ExplainCard}

            \begin{ExplainCard}{calling others’ names}[idiom][C1]
            \EN{To insult or criticize someone with offensive words.}
            \SY{insult; abuse; slander}
            \VI{chửi rủa, bêu xấu người khác.}
            \EX{They were calling each other names during the argument.}
            \EX{Bullying often involves calling others’ names.}
            \CO{start calling names; stop calling names}
            \end{ExplainCard}

            \begin{ExplainCard}{innocuous}[adj][C1]
            \EN{Harmless; not offensive or dangerous.}
            \SY{harmless; inoffensive; safe}
            \VI{vô hại, không gây xúc phạm.}
            \EX{The remark was innocuous and not intended to offend.}
            \EX{These drugs are relatively innocuous.}
            \CO{innocuous comment; innocuous habit}
            \end{ExplainCard}

            \begin{ExplainCard}{displeased with}[phrase][C1]
            \EN{Annoyed or unhappy about something.}
            \SY{dissatisfied; unhappy; annoyed}
            \VI{không hài lòng về.}
            \EX{She was displeased with his behavior.}
            \EX{Customers were displeased with the service.}
            \CO{displeased with sb/sth}
            \end{ExplainCard}

            \begin{ExplainCard}{sensationalize}[v][C1]
            \EN{To present information in a way that provokes public interest, often exaggerating.}
            \SY{exaggerate; dramatize}
            \VI{giật gân, thổi phồng.}
            \EX{The media tends to sensationalize crime stories.}
            \EX{They sensationalized the scandal for ratings.}
            \CO{sensationalize the news; sensationalized report}
            \end{ExplainCard}

            \begin{ExplainCard}{spread like wildfire}[idiom][C1]
            \EN{To spread extremely quickly.}
            \SY{spread rapidly; go viral}
            \VI{lan nhanh như cháy rừng.}
            \EX{The rumor spread like wildfire through the town.}
            \EX{The video spread like wildfire on social media.}
            \CO{spread like wildfire}
            \end{ExplainCard}

            \begin{ExplainCard}{victimize}[v][C1]
            \EN{To treat someone unfairly or make them suffer.}
            \SY{persecute; mistreat; oppress}
            \VI{ngược đãi, biến ai thành nạn nhân.}
            \EX{The minority group was victimized by unfair laws.}
            \EX{She felt victimized by the criticism.}
            \CO{victimize sb; be victimized by sth}
            \end{ExplainCard}

            \begin{ExplainCard}{do not have the faintest idea about}[idiom][B2]
            \EN{To not know anything about something.}
            \SY{no clue; no idea}
            \VI{hoàn toàn không biết gì.}
            \EX{I don’t have the faintest idea about physics.}
            \EX{He didn’t have the faintest idea about what happened.}
            \CO{not have the faintest idea about sth}
            \end{ExplainCard}

            \begin{ExplainCard}{barrage}[n][C1]
            \EN{A great number of complaints, criticisms, or questions delivered quickly.}
            \SY{torrent; flood; avalanche}
            \VI{một loạt dồn dập (chỉ trích, câu hỏi...).}
            \EX{The minister faced a barrage of criticism.}
            \EX{She received a barrage of questions from reporters.}
            \CO{barrage of criticism; barrage of questions}
            \end{ExplainCard}

            \begin{ExplainCard}{driven to despair}[phrase][C1]
            \EN{Made extremely hopeless or unhappy.}
            \SY{pushed to hopelessness; forced into misery}
            \VI{bị dồn vào tuyệt vọng.}
            \EX{She was driven to despair after losing her job.}
            \EX{Financial problems drove him to despair.}
            \CO{be driven to despair by sth}
            \end{ExplainCard}
        \end{VocabExplain}

    \noindent
    \textbf{Part 2.}
    \begin{qa}{Describe something you liked very much which you bought for your home. You should say:
    \begin{itemize}
        \item What you bought
        \item When and where you bought it
        \item Why you chose this particular thing
        \item and explain why you liked it so much
    \end{itemize}}

    If you ask me to describe something I could \textbf{give my right arm for}, I would not hesitate to talk about my recently-bought sofa made by Ashley, a \textbf{leading} furniture brand in the U.S. I possessed it \textbf{a fortnight} ago. At that time, there was a \textbf{promotional campaign} in “Pho Xinh”, one of the most famous Hanoi-based furniture \textbf{retailers}, and the store managers had decided to \textbf{slash prices} to \textbf{increase the volume of sales}. I decided to buy it \textbf{at first glance} because I thought that it was \textbf{good value for money}. Hence, I \textbf{snapped up a bargain} to own it for less than \$1,500. 

    There are several reasons why I \textbf{glom onto} it. Firstly, it’s L-shaped, which is definitely the most practical to \textbf{seat} many people in a spacious living room. So it’s great when I \textbf{have friends over} because it means we can all sit together. Secondly, this sofa is quite \textbf{comfy} and made of \textbf{suede}, my favorite material. Moreover, I can \textbf{sprawl on it} to watch TV in comfort. Thirdly, its color is \textbf{beige}, which \textbf{goes well with} the interior of the living room. Moreover, beige is quite a warm and natural color so it helps create a \textbf{homely} atmosphere. All in all, I have been satisfied with it so far.
    \end{qa}

        \begin{VocabExplain}[Part 2]
            \begin{ExplainCard}{give my right arm for}[idiom][C1]
            \EN{To be willing to give up something very valuable in order to get or do something.}
            \SY{desire greatly; long for}
            \VI{rất khao khát, sẵn sàng đánh đổi nhiều thứ để có được.}
            \EX{I’d give my right arm for a chance to study abroad.}
            \EX{He would give his right arm for a job like that.}
            \CO{give one’s right arm for sth}
            \end{ExplainCard}

            \begin{ExplainCard}{a fortnight}[n][B2]
            \EN{A period of two weeks.}
            \SY{two weeks}
            \VI{hai tuần lễ.}
            \EX{They stayed with us for a fortnight.}
            \EX{The project will be finished within a fortnight.}
            \CO{in a fortnight; every fortnight}
            \end{ExplainCard}

            \begin{ExplainCard}{slash prices}[v][C1]
            \EN{To reduce prices drastically.}
            \SY{cut; reduce; lower}
            \VI{giảm giá mạnh.}
            \EX{The store slashed prices during the holiday sale.}
            \EX{They had to slash prices to attract customers.}
            \CO{slash prices; slash costs}
            \end{ExplainCard}

            \begin{ExplainCard}{at first glance}[idiom][B2]
            \EN{Immediately upon first seeing or considering something.}
            \SY{at first sight; instantly}
            \VI{ngay cái nhìn đầu tiên.}
            \EX{At first glance, the problem looked easy.}
            \EX{He fell in love at first glance.}
            \CO{at first glance}
            \end{ExplainCard}

            \begin{ExplainCard}{good value for money}[phrase][B2]
            \EN{Something well worth the money spent on it.}
            \SY{worthwhile; cost-effective}
            \VI{đáng đồng tiền bát gạo.}
            \EX{This phone is good value for money.}
            \EX{The hotel offers good value for money.}
            \CO{be good value for money}
            \end{ExplainCard}

            \begin{ExplainCard}{snap up a bargain}[idiom][C1]
            \EN{To buy something quickly because it is cheap or good value.}
            \SY{seize; grab quickly}
            \VI{chớp lấy cơ hội mua rẻ.}
            \EX{I snapped up a bargain in the sale.}
            \EX{Shoppers snapped up bargains during the clearance.}
            \CO{snap up a bargain}
            \end{ExplainCard}

            \begin{ExplainCard}{glom onto}[phr.v][C1]
            \EN{To become very attached to or enthusiastic about something.}
            \SY{cling to; latch onto}
            \VI{gắn bó, yêu thích.}
            \EX{He quickly glommed onto the idea.}
            \EX{She glommed onto the new fashion trend.}
            \CO{glom onto sth}
            \end{ExplainCard}

            \begin{ExplainCard}{comfy}[adj][B2]
            \EN{Informal for comfortable.}
            \SY{comfortable; cozy; pleasant}
            \VI{thoải mái, dễ chịu.}
            \EX{This chair is really comfy.}
            \EX{I feel so comfy in this sweater.}
            \CO{comfy sofa; comfy clothes}
            \end{ExplainCard}

            \begin{ExplainCard}{suede}[n][B2]
            \EN{A type of soft leather with a slightly rough surface.}
            \SY{soft leather}
            \VI{da lộn.}
            \EX{She bought a pair of suede shoes.}
            \EX{The sofa was upholstered in suede.}
            \CO{suede shoes; suede jacket}
            \end{ExplainCard}

            \begin{ExplainCard}{sprawl on}[phr.v][C1]
            \EN{To lie or sit with arms and legs stretched out.}
            \SY{stretch out; lounge}
            \VI{nằm dài ra thoải mái.}
            \EX{He sprawled on the sofa watching TV.}
            \EX{Children sprawled on the grass in the park.}
            \CO{sprawl on the bed/sofa}
            \end{ExplainCard}

            \begin{ExplainCard}{beige}[n/adj][B2]
            \EN{A light brownish-yellow color.}
            \SY{tan; light brown}
            \VI{màu be.}
            \EX{She wore a beige coat.}
            \EX{The walls were painted beige.}
            \CO{beige color; beige fabric}
            \end{ExplainCard}

            \begin{ExplainCard}{goes well with}[phrase][B2]
            \EN{To match or look good together.}
            \SY{match; complement}
            \VI{hợp với, phối hợp tốt.}
            \EX{This shirt goes well with your trousers.}
            \EX{The wine goes well with seafood.}
            \CO{goes well with sth}
            \end{ExplainCard}

            \begin{ExplainCard}{homely}[adj][C1]
            \EN{(Of a place) pleasant and comfortable in a simple way.}
            \SY{cozy; snug; welcoming}
            \VI{ấm cúng, giản dị.}
            \EX{The house has a homely atmosphere.}
            \EX{Her homely kitchen was very inviting.}
            \CO{homely atmosphere; homely environment}
            \end{ExplainCard}
        \end{VocabExplain}

    \noindent
    \textbf{Part 3.}
    \begin{qa}{Why do some people buy lots of things for their home?}
    Naturally, home is where the heart is, which is why people always want to complement their house with things and decorations. After hours of following a \textbf{rigorous} schedule, house is the place where family members could \textbf{get something off their chest}, and enjoy family gatherings. By contrast, a bare house could bring a sense of \textbf{emptiness}.
    \end{qa}

    \begin{qa}{Do you think it is very expensive to make a home look nice?}
    Well, it is quite dependable. Many may \textbf{pay top dollar} to get a collection of \textbf{antiques}, which could make their house look more \textbf{elegant} and \textbf{fancy}. However, other people resign themselves to forking over a small amount of their budget to buy second-hand furniture along with stuffs like \textbf{knick knacks} to decorate their house. That a house looks great depends on whether the ornamental items fit in the surrounding or not.
    \end{qa}

    \begin{qa}{Why don’t some people care about how their home looks?}
    I consider myself a generally \textbf{neat} and organized person, so I would like to \textbf{tidy up} my room whenever I have free time to make it \textbf{spotless}. Nonetheless, there are people who do not \textbf{give a hoot on sprucing up} their house, making their house so dusty. This might be because they are \textbf{insanely busy}, and their jobs are \textbf{at the forefront of their minds}. \textbf{In their book}, maybe their house is just a place for them to get some sleep so there’s no need to care about it.
    \end{qa}

    \begin{qa}{In what ways is living in a flat/apartment better than living in a house?}
    Unlike houses, \textbf{apartment complexes} are generally built with specific amenities such as pools, convenience stores and laundry facilities on the \textbf{premises} or at the least in the \textbf{proximity}. Therefore, apartment living can prove to be a very convenient living arrangement. Moreover, multi-unit dwellings, in contrast to detached houses, are the safer locations for single women, children, families and the elderly. At some apartment blocks, strangers are asked to leave their personal identity cards at the reception before being allowed to go up stairs. This proves to be much safer compared to living in a house where strangers could break in anytime.
    \end{qa}

    \begin{qa}{Do you think homes will look different in the future?}
    Interestingly, I guess home wind turbines and home use of \textbf{geothermal energy} will become the norm in the coming years as energy independence has been one of national priorities. Undoubtedly, humans will \textbf{take advantage of} future robots to do chores such as doing the washing-up and tidying up the house and so on. These days, scientists have made great \textbf{strides} in developing more realistic and functional robots that can recognize human speech and respond to it or do specific tasks around the house.
    \end{qa}

    \begin{qa}{Do you agree that the kinds of homes people prefer change as they get older?}
    I would say yes. Basically, living in a \textbf{magnificent} house with \textbf{first-class} facilities is a dream for many young people in the city. As people are get older, they might want to relocate to rural areas where there are less \textbf{suffocating} fumes and lengthy traffic. And living in a modest house will be the option for old people as they cannot do the heavy housework of the big ones.
    \end{qa}

        \begin{VocabExplain}[Part 3]
            \begin{ExplainCard}{rigorous}[adj][C1]
            \EN{Extremely thorough, accurate, or strict.}
            \SY{strict; severe; demanding}
            \VI{nghiêm ngặt, khắt khe.}
            \EX{She followed a rigorous training schedule.}
            \EX{The research was done with rigorous methods.}
            \CO{rigorous schedule; rigorous standards}
            \end{ExplainCard}

            \begin{ExplainCard}{get something off one’s chest}[idiom][C1]
            \EN{To tell someone about something that has been worrying you or making you upset.}
            \SY{confess; reveal; unload}
            \VI{giãi bày, trút bỏ tâm sự.}
            \EX{I had to get it off my chest and tell her the truth.}
            \EX{Talking to a friend helped me get my worries off my chest.}
            \CO{get sth off your chest}
            \end{ExplainCard}

            \begin{ExplainCard}{emptiness}[n][B2]
            \EN{The state of containing nothing, or a feeling of loneliness or lack of purpose.}
            \SY{void; blankness; hollowness}
            \VI{sự trống rỗng.}
            \EX{She felt a sense of emptiness after her children left home.}
            \EX{The emptiness of the desert stretched out before them.}
            \CO{feeling of emptiness; emotional emptiness}
            \end{ExplainCard}

            \begin{ExplainCard}{pay top dollar}[idiom][C1]
            \EN{To pay a lot of money for something, usually of high quality or rare.}
            \SY{pay a fortune; spend heavily}
            \VI{trả giá rất cao.}
            \EX{He paid top dollar for that vintage car.}
            \EX{Fans are willing to pay top dollar for tickets.}
            \CO{pay top dollar for sth}
            \end{ExplainCard}

            \begin{ExplainCard}{antiques}[n][B2]
            \EN{Objects, such as furniture, that are valuable because they are old.}
            \SY{collectibles; relics}
            \VI{đồ cổ.}
            \EX{She collects antiques from around the world.}
            \EX{Antiques are often displayed in museums.}
            \CO{antique furniture; antique shop}
            \end{ExplainCard}

            \begin{ExplainCard}{elegant}[adj][B2]
            \EN{Graceful and stylish in appearance or manner.}
            \SY{graceful; refined; sophisticated}
            \VI{thanh lịch, tao nhã.}
            \EX{She wore an elegant black dress.}
            \EX{The hotel lobby was elegantly decorated.}
            \CO{elegant design; elegant solution}
            \end{ExplainCard}

            \begin{ExplainCard}{fancy}[adj][B2]
            \EN{Unusually decorative or elaborate.}
            \SY{ornate; elaborate; luxurious}
            \VI{cầu kỳ, sang trọng.}
            \EX{He bought a fancy car.}
            \EX{They stayed at a fancy hotel.}
            \CO{fancy restaurant; fancy clothes}
            \end{ExplainCard}

            \begin{ExplainCard}{knick knacks}[n][C1]
            \EN{Small worthless objects, especially ornaments.}
            \SY{trinkets; ornaments; baubles}
            \VI{đồ lặt vặt, đồ trang trí nhỏ.}
            \EX{The shelves were full of knick knacks.}
            \EX{She collects knick knacks from her travels.}
            \CO{decorative knick knacks; collect knick knacks}
            \end{ExplainCard}

            \begin{ExplainCard}{neat}[adj][B1]
            \EN{Arranged in an orderly and tidy way.}
            \SY{tidy; organized; orderly}
            \VI{ngăn nắp, gọn gàng.}
            \EX{He always keeps his desk neat.}
            \EX{The room was neat and clean.}
            \CO{neat handwriting; neat appearance}
            \end{ExplainCard}

            \begin{ExplainCard}{tidy up}[phr.v][B1]
            \EN{To make a place look better by putting things in the correct place.}
            \SY{clean up; organize}
            \VI{dọn dẹp, làm gọn gàng.}
            \EX{She tidied up her room before the guests arrived.}
            \EX{I spent the afternoon tidying up the garden.}
            \CO{tidy up a room; tidy up after sb}
            \end{ExplainCard}

            \begin{ExplainCard}{spotless}[adj][C1]
            \EN{Completely clean; without any dirt or stains.}
            \SY{immaculate; pristine; clean}
            \VI{sạch bóng, tinh tươm.}
            \EX{Her kitchen is always spotless.}
            \EX{The hotel rooms were spotless and tidy.}
            \CO{spotless house; spotless reputation}
            \end{ExplainCard}

            \begin{ExplainCard}{give a hoot on sprucing up}[idiom][C1]
            \EN{(usually negative) To care about improving or decorating something.}
            \SY{bother; care; pay attention}
            \VI{quan tâm (trang hoàng, làm đẹp).}
            \EX{He doesn’t give a hoot on sprucing up his house.}
            \EX{They didn’t give a hoot on sprucing up their office.}
            \CO{not give a hoot on sprucing up sth}
            \end{ExplainCard}

            \begin{ExplainCard}{insanely busy}[phrase][C1]
            \EN{Extremely busy.}
            \SY{overwhelmed; swamped}
            \VI{bận rộn kinh khủng.}
            \EX{I’ve been insanely busy at work this week.}
            \EX{She is insanely busy preparing for the wedding.}
            \CO{insanely busy schedule}
            \end{ExplainCard}

            \begin{ExplainCard}{at the forefront of one’s mind}[idiom][C1]
            \EN{Being the most important thing someone is thinking about.}
            \SY{top priority; main concern}
            \VI{ưu tiên hàng đầu trong tâm trí.}
            \EX{Climate change is at the forefront of global discussions.}
            \EX{Her children’s safety is at the forefront of her mind.}
            \CO{at the forefront of debate}
            \end{ExplainCard}

            \begin{ExplainCard}{in their book}[idiom][C1]
            \EN{In someone’s opinion.}
            \SY{in their view; as far as they are concerned}
            \VI{theo ý kiến của họ.}
            \EX{In my book, honesty is the most important quality.}
            \EX{He’s a hero in their book.}
            \CO{in my book; in their book}
            \end{ExplainCard}

            \begin{ExplainCard}{apartment complexes}[n][B2]
            \EN{Large groups of apartment buildings managed as a single community.}
            \SY{housing estate; block of flats}
            \VI{khu chung cư.}
            \EX{They moved into a new apartment complex.}
            \EX{The apartment complex has a gym and pool.}
            \CO{modern apartment complex}
            \end{ExplainCard}

            \begin{ExplainCard}{premises}[n][C1]
            \EN{The land and buildings that a business or organization uses.}
            \SY{site; grounds; property}
            \VI{khuôn viên, cơ sở.}
            \EX{No smoking is allowed on the school premises.}
            \EX{The company moved to new premises downtown.}
            \CO{school premises; company premises}
            \end{ExplainCard}

            \begin{ExplainCard}{proximity}[n][C1]
            \EN{The state of being close to something in distance or time.}
            \SY{nearness; closeness}
            \VI{sự gần gũi, khoảng cách gần.}
            \EX{The hotel is in close proximity to the beach.}
            \EX{The proximity of the two events caused confusion.}
            \CO{in close proximity; proximity to sth}
            \end{ExplainCard}

            \begin{ExplainCard}{geothermal energy}[n][C1]
            \EN{Heat energy that comes from inside the Earth.}
            \SY{earth heat power}
            \VI{năng lượng địa nhiệt.}
            \EX{Iceland uses geothermal energy for heating.}
            \EX{Geothermal energy is a clean renewable source.}
            \CO{geothermal energy source}
            \end{ExplainCard}

            \begin{ExplainCard}{take advantage of}[phr.v][B2]
            \EN{To use the good things in a situation.}
            \SY{make use of; exploit}
            \VI{tận dụng.}
            \EX{She took advantage of the holiday to relax.}
            \EX{Students should take advantage of the library facilities.}
            \CO{take advantage of sth}
            \end{ExplainCard}

            \begin{ExplainCard}{strides}[n][C1]
            \EN{Large advances or progress.}
            \SY{progress; breakthroughs; improvement}
            \VI{bước tiến, sự phát triển vượt bậc.}
            \EX{The company made great strides in AI research.}
            \EX{Medical science has taken huge strides in recent years.}
            \CO{make strides in sth}
            \end{ExplainCard}

            \begin{ExplainCard}{magnificent}[adj][C1]
            \EN{Extremely impressive or beautiful.}
            \SY{splendid; grand; glorious}
            \VI{tráng lệ, lộng lẫy.}
            \EX{They visited a magnificent cathedral.}
            \EX{She gave a magnificent performance.}
            \CO{magnificent view; magnificent building}
            \end{ExplainCard}

            \begin{ExplainCard}{first-class}[adj][B2]
            \EN{Of the highest quality.}
            \SY{excellent; outstanding; premium}
            \VI{hạng nhất, chất lượng cao.}
            \EX{She received first-class service at the hotel.}
            \EX{He graduated with first-class honors.}
            \CO{first-class facilities; first-class degree}
            \end{ExplainCard}

            \begin{ExplainCard}{suffocating}[adj][C1]
            \EN{Making it hard to breathe or creating discomfort due to lack of air.}
            \SY{stifling; oppressive}
            \VI{ngột ngạt, nghẹt thở.}
            \EX{The suffocating heat made it impossible to work.}
            \EX{She felt suffocating pressure from expectations.}
            \CO{suffocating atmosphere; suffocating fumes}
            \end{ExplainCard}
        \end{VocabExplain}

    \begin{VocabHighlights}
        \VH{onslaught}{(n) something resembling such an attack}{(danh từ) hàng đàn, lũ lượt}
        \VH{de facto}{(adj) existing in fact, although perhaps not intended, legal, or accepted}{(tính từ) rõ ràng ai cũng biết nhưng sai về mặt luật pháp}
        \VH{stay tuned to}{(idiom) used to say that you should look or listen for more information later}{(thành ngữ) luôn cập nhật, theo kịp diễn biến}
        \VH{in the blink of an eye}{(idiom) extremely quick}{(thành ngữ) cực nhanh}
        \VH{to call others’ names}{(idiom) to insult somebody by saying unpleasant things}{(thành ngữ) sỉ nhục ai}
        \VH{innocuous}{(adj) not intended or likely to offend or upset anyone}{(tính từ) vô thưởng vô phạt, không hại ai}
        \VH{displeased}{(adj) feeling upset, annoyed or not satisfied}{(tính từ) cảm thấy bất mãn}
        \VH{to spread like wildfire}{(idiom) to spread with great speed}{(thành ngữ) lan truyền nhanh}
        \VH{to sensationalize}{(v) present information in a way that provokes excitement at the expense of accuracy}{(động từ) làm trầm trọng hóa}
        \VH{to be victimized for}{(p2) to become a victim of}{(phân từ 2) là nạn nhân của}
        \VH{not have the faintest idea about}{(phrase) have no clue}{(cụm từ) không hiểu tí nào}
        \VH{a barrage of}{(phrase) a great number of complaints or criticisms suddenly directed at someone}{(cụm từ) một số lượng lớn câu hỏi, chỉ trích nhằm vào ai cùng lúc}
        \VH{to be driven to despair}{(phrase) to be hopeless}{(cụm từ) trở nên tuyệt vọng}
        \VH{give my right arm for something}{(idiom) like something very much}{(thành ngữ) thích cái gì rất nhiều}
        \VH{leading}{(adj) most important or most successful}{(tính từ) hàng đầu}
        \VH{a fortnight}{(phrase) 2 weeks}{(cụm từ) 2 tuần}
        \VH{promotional campaign}{(phrase) a series of advertisements using various marketing tools that share similar messages to promote a business or event}{(cụm từ) chiến dịch quảng bá}
        \VH{retailer}{(n) a person or business that sells goods to the public}{(danh từ) doanh nghiệp bán lẻ}
        \VH{slash prices}{(phrase) reduce prices}{(cụm từ) giảm giá}
        \VH{to increase the volume of sales}{(phrase) sell more products}{(cụm từ) bán được nhiều hàng}
        \VH{at first glance}{(idiom) immediately; with only a quick look}{(thành ngữ) ngay lập tức, nhìn thoáng qua}
        \VH{to be good value for money}{(idiom) something makes the best out of money}{(thành ngữ) đáng giá tiền}
        \VH{to snap up a bargain}{(idiom) grab a deal}{(thành ngữ) chộp ngay cơ hội giảm giá}
        \VH{to glom onto}{(phrasal verb) to develop a strong interest in something}{(cụm động từ) cực kỳ thích thú}
        \VH{to seat}{(v) to give somebody a place to sit; to sit down in a place}{(động từ) ngồi được}
        \VH{to have somebody over}{(phrasal verb) have somebody drop in your house}{(cụm động từ) có ai ghé qua chơi}
        \VH{comfy}{(adj) comfortable}{(tính từ) thoải mái}
        \VH{suede}{(n) soft leather with a surface like velvet on one side, used especially for making clothes and shoes}{(danh từ) da lộn}
        \VH{to sprawl (out) on}{(phr.v) to lie or sit with your arms or legs stretched out in a lazy or careless way}{(cụm động từ) nằm ườn ra thư giãn}
        \VH{beige}{(n) light yellow-brown in colour}{(danh từ) màu be, vàng nhạt}
        \VH{to go well with}{(phr.v) to match}{(cụm động từ) phù hợp với}
        \VH{homely}{(adj) making you feel comfortable, as if you were in your own home}{(tính từ) thoải mái như khi ở nhà}
        \VH{rigorous}{(adj) careful to look at or consider every part of something to make certain it is correct or safe}{(tính từ) nghiêm ngặt}
        \VH{to pay top dollar}{(idiom) to pay a lot of money}{(thành ngữ) tiêu nhiều tiền}
        \VH{to get something off their chest}{(phrase) say something that one has wanted to say for a long time, resulting in a feeling of relief}{(cụm từ) giải bày tâm sự}
        \VH{emptiness}{(n) a sad feeling of having no emotion or purpose}{(danh từ) sự trống trải}
        \VH{antique}{(n) (of furniture, jewellery, etc.) old and often valuable}{(danh từ) đồ cổ}
        \VH{elegant}{(adj) attractive and showing a good sense of style}{(tính từ) thanh lịch; tao nhã}
        \VH{to fancy}{(v) decorative or complicated}{(động từ) trang hoàng}
        \VH{knick knacks}{(n) a small decorative object in a house}{(danh từ) đồ trang trí nhỏ}
        \VH{neat}{(adj) tidy and in order; carefully done or arranged}{(tính từ) khéo léo}
        \VH{to tidy up}{(phr.v) clean up}{(cụm động từ) dọn dẹp phòng}
        \VH{spotless}{(adj) perfectly clean}{(tính từ) không một vết bẩn}
        \VH{not give a hoot on}{(idiom) not care at all}{(thành ngữ) không quan tâm tí nào}
        \VH{to spruce up}{(phr.v) to make somebody/something clean and neat}{(cụm động từ) dọn dẹp cho sạch}
        \VH{to be insanely busy}{(phrase) to be extremely busy}{(cụm từ) bận điên cuồng}
        \VH{at the forefront of somebody’s mind}{(idiom) to be what someone is thinking about most}{(thành ngữ) chiếm hết tâm trí ai}
        \VH{in one’s book}{(idiom) according to one’s opinion or way of thinking}{(thành ngữ) theo ý ai}
        \VH{apartment complexes}{(phrase) a group of buildings that contain apartments}{(cụm từ) tổ hợp chung cư}
        \VH{the premises}{(n) the building and land near to it that a business owns or uses}{(danh từ) toà nhà}
        \VH{proximity}{(n) the state of being near in distance or time}{(danh từ) khu vực phụ cận}
        \VH{geothermal energy}{(n) thermal energy}{(danh từ) nhiệt năng}
        \VH{to take advantage of}{(phrase) make good use of the opportunities offered by (something)}{(cụm từ) tận dụng}
        \VH{stride}{(n) an important positive development}{(danh từ) bước tiến}
        \VH{magnificent}{(adj) very good, beautiful, or deserving to be admired}{(tính từ) hoành tráng, đẹp}
        \VH{first-class}{(adj) excellent}{(tính từ) bậc nhất}
        \VH{suffocating}{(adj) something that is suffocating makes you feel uncomfortably hot or unable to breathe}{(tính từ) ngạt thở}
    \end{VocabHighlights}
    \end{test}

    \begin{test}{TEST 3}
    \noindent
    \textbf{Part 1. Neighbours}
    \begin{qa}{How often do you see your neighbours? [Why/Why not?]}
    In general, I do not often interact with my neighbors. On weekdays, I am \textbf{as busy as a bee}, leaving for work early in the morning and getting back home late at night. At weekends, I enjoy not only \textbf{having a lie-in} but also spending quality time with family by driving them to places of interest. That explains why I lack time to see my neighbors.
    \end{qa}

    \begin{qa}{Do you invite your neighbours to your home? [Why/Why not?]}
    As I hardly know anyone around me, I haven’t invited my neighbors to come over my home yet. Maybe a rare occasion when I asked one to drop by was when my child got a fever. I knew a pediatrician living nearby, hence I asked him to diagnose my kid and give a prescription only.
    \end{qa}

    \begin{qa}{Do you think you are a good neighbour? [Why/Why not?]}
    I \textbf{do not have the vaguest idea} how people around assess me. However, in my opinion, I am a good one because I neither \textbf{stick my nose in others’ business} nor \textbf{make up} stories about others. If there’s anyone asking for volunteer work such as cleaning up the surroundings, I never mind \textbf{getting down to doing it in an instant}.
    \end{qa}

    \begin{qa}{Has a neighbour ever helped you? [Why/Why not?]}
    Yes, like I said above, he \textbf{lent me a helping hand} to cure my daughter’s diseases, not only a cold fever but also a number of other ones such as measles. Besides, I’m also not an expert on repairing household appliances so when anything is out of order, I may ask some technicians to fix it at a reasonable price.
    \end{qa}

        \begin{VocabExplain}[Part 1]
            \begin{ExplainCard}{as busy as a bee}[idiom][B2]
            \EN{Very active and busy, always moving from task to task.}
            \SY{hard-working; industrious; occupied}
            \VI{bận rộn như ong.}
            \EX{She’s as busy as a bee with her new business.}
            \EX{During exam week, students are as busy as bees.}
            \CO{be as busy as a bee}
            \end{ExplainCard}

            \begin{ExplainCard}{have a lie-in}[phrase][B2]
            \EN{To stay in bed later than usual in the morning.}
            \SY{sleep late; rest}
            \VI{ngủ nướng.}
            \EX{On Sundays I usually have a lie-in until 10 a.m.}
            \EX{After a long week, he enjoys having a lie-in.}
            \CO{enjoy a lie-in; weekend lie-in}
            \end{ExplainCard}

            \begin{ExplainCard}{do not have the vaguest idea}[idiom][C1]
            \EN{To have absolutely no knowledge or understanding of something.}
            \SY{no clue; no idea}
            \VI{hoàn toàn không biết.}
            \EX{I don’t have the vaguest idea where she went.}
            \EX{He didn’t have the vaguest idea about the solution.}
            \CO{not have the vaguest idea about sth}
            \end{ExplainCard}

            \begin{ExplainCard}{stick one’s nose in others’ business}[idiom][C1]
            \EN{To interfere in other people’s affairs.}
            \SY{meddle; interfere; intrude}
            \VI{xía mũi vào chuyện người khác.}
            \EX{Don’t stick your nose in my business!}
            \EX{She’s always sticking her nose in other people’s lives.}
            \CO{stick one’s nose into sth}
            \end{ExplainCard}

            \begin{ExplainCard}{make up}[phr.v][B1]
            \EN{To invent a story, excuse, or lie.}
            \SY{fabricate; invent; concoct}
            \VI{bịa ra, dựng chuyện.}
            \EX{He made up an excuse for being late.}
            \EX{Don’t make up stories about your classmates.}
            \CO{make up a story; make up an excuse}
            \end{ExplainCard}

            \begin{ExplainCard}{get down to doing sth}[phrase][B2]
            \EN{To start doing something seriously or with focus.}
            \SY{begin; start; tackle}
            \VI{bắt tay vào làm việc gì.}
            \EX{It’s time to get down to doing homework.}
            \EX{They finally got down to discussing the main issue.}
            \CO{get down to business; get down to work}
            \end{ExplainCard}

            \begin{ExplainCard}{in an instant}[idiom][B2]
            \EN{Very quickly; immediately.}
            \SY{instantly; at once; right away}
            \VI{ngay lập tức.}
            \EX{The news spread in an instant.}
            \EX{He disappeared in an instant.}
            \CO{in an instant; vanish in an instant}
            \end{ExplainCard}

            \begin{ExplainCard}{lend sb a helping hand}[idiom][B2]
            \EN{To help someone with something.}
            \SY{assist; aid; support}
            \VI{giúp đỡ ai đó.}
            \EX{She lent me a helping hand with the project.}
            \EX{He always lends a helping hand to his neighbors.}
            \CO{lend a helping hand; give a helping hand}
            \end{ExplainCard}
        \end{VocabExplain}

    \noindent
    \textbf{Part 2.}
    \begin{qa}{Describe a very difficult task that you succeeded in doing as part of your work or studies.}
    \begin{itemize}
        \item What task you did  
        \item Why this task was very difficult  
        \item How you worked in this task  
        \item and explain how you felt when you had successfully completed this task.  
    \end{itemize}

    \textbf{In all sincerity}, I am working as an IELTS trainer at the Institution of American Education. It is built by overseas students and its mission is to open the doors for students to gain access to quality education through scholarships. Although most of the students were \textbf{more or less} hard-working, their writing skills were unsatisfactory so there was room for improvement.  

    In order to help students hone their writing skills, I was appointed as a trainer for a period of 4 weeks. This \textbf{presented a challenge} for me because at that time, I was just a newbie at the workplace and I did have \textbf{no clue about} what they had been taught before. More seriously, students were mostly in high school, so they might not be mature enough to \textbf{make heads or tails of this world}. They \textbf{struggled to come up with} ideas for some questions because they were \textbf{beyond their ken}.  

    As you can probably guess, improving writing is time-consuming because learners need to focus on many aspects such as grammar accuracy, vocabulary range, coherence and cohesion, let alone relevant ideas. I adopted some measures to help improve the situation. First, I sent them a collection of samples carefully written by examiners. Thanks to this collection, they could have a clear understanding of the format and how to develop ideas. They could \textbf{accumulate} more academic words through the sample essays as well. Second, I asked them to submit their essays on a weekly basis for correction. I made an attempt to give them feedback and recommendations on how to maximize their band score. Luckily, all of them did not \textbf{let me down} when they got at least 6.5 in IELTS Writing.  

    I still remember the day when they informed me of their results. I \textbf{burst into tears} because I was \textbf{on cloud nine}, and I \textbf{took great pride in} them.
    \end{qa}

        \begin{VocabExplain}[Part 2]
            \begin{ExplainCard}{in all sincerity}[phrase][C1]
            \EN{Used to emphasize that what you are saying is honest and genuine.}
            \SY{honestly; truthfully; sincerely}
            \VI{thành thật mà nói.}
            \EX{In all sincerity, I don’t think this plan will work.}
            \EX{She spoke in all sincerity about her mistakes.}
            \CO{in all sincerity + clause}
            \end{ExplainCard}

            \begin{ExplainCard}{more or less}[phrase][B2]
            \EN{Almost; approximately; nearly.}
            \SY{almost; roughly; practically}
            \VI{gần như, xấp xỉ.}
            \EX{He’s more or less recovered from his illness.}
            \EX{The project is more or less finished.}
            \CO{be more or less done; more or less complete}
            \end{ExplainCard}

            \begin{ExplainCard}{present a challenge}[phrase][B2]
            \EN{To be difficult and test someone’s abilities.}
            \SY{pose a difficulty; create an obstacle}
            \VI{tạo ra thách thức.}
            \EX{The new job presented a challenge to him.}
            \EX{Teaching young children presents a challenge for any teacher.}
            \CO{present a challenge to sb; present a major challenge}
            \end{ExplainCard}

            \begin{ExplainCard}{no clue about}[phrase][B2]
            \EN{To have no knowledge or understanding of something.}
            \SY{no idea; no knowledge}
            \VI{không biết gì về.}
            \EX{I have no clue about how to solve this.}
            \EX{She had no clue about his real intentions.}
            \CO{have no clue about sth}
            \end{ExplainCard}

            \begin{ExplainCard}{make heads or tails of}[idiom][C1]
            \EN{To understand something, usually something complicated.}
            \SY{understand; grasp; figure out}
            \VI{hiểu được (thường dùng phủ định).}
            \EX{I couldn’t make heads or tails of the report.}
            \EX{He can’t make heads or tails of this math problem.}
            \CO{can’t make heads or tails of sth}
            \end{ExplainCard}

            \begin{ExplainCard}{struggle to come up with}[phrase][B2]
            \EN{To have difficulty thinking of an idea or answer.}
            \SY{find hard to think; labor to produce}
            \VI{khó khăn trong việc nghĩ ra.}
            \EX{She struggled to come up with an excuse.}
            \EX{They struggled to come up with new ideas.}
            \CO{struggle to come up with an answer/idea}
            \end{ExplainCard}

            \begin{ExplainCard}{beyond one’s ken}[idiom][C2]
            \EN{Outside the range of what someone knows or understands.}
            \SY{outside comprehension; out of reach}
            \VI{vượt ngoài tầm hiểu biết.}
            \EX{Quantum physics is beyond my ken.}
            \EX{Some mysteries remain beyond human ken.}
            \CO{beyond one’s ken}
            \end{ExplainCard}

            \begin{ExplainCard}{accumulate}[v][C1]
            \EN{To gather or build up something gradually over time.}
            \SY{collect; amass; gather}
            \VI{tích lũy.}
            \EX{He accumulated wealth through investments.}
            \EX{Over the years, she accumulated knowledge in the field.}
            \CO{accumulate wealth; accumulate experience; accumulate vocabulary}
            \end{ExplainCard}

            \begin{ExplainCard}{let sb down}[phr.v][B2]
            \EN{To disappoint someone by failing to do what they expected.}
            \SY{disappoint; fail}
            \VI{làm ai thất vọng.}
            \EX{I promised not to let her down.}
            \EX{He really let me down when he forgot my birthday.}
            \CO{let sb down badly; never let sb down}
            \end{ExplainCard}

            \begin{ExplainCard}{burst into tears}[idiom][B2]
            \EN{To suddenly start crying.}
            \SY{start crying; break down}
            \VI{oà khóc, bật khóc.}
            \EX{She burst into tears when she heard the news.}
            \EX{He burst into tears of joy after the victory.}
            \CO{burst into tears of joy/sadness}
            \end{ExplainCard}

            \begin{ExplainCard}{on cloud nine}[idiom][C1]
            \EN{Extremely happy.}
            \SY{overjoyed; delighted; ecstatic}
            \VI{vui sướng tột cùng.}
            \EX{She was on cloud nine after passing the exam.}
            \EX{He’s been on cloud nine since his wedding.}
            \CO{be on cloud nine}
            \end{ExplainCard}

            \begin{ExplainCard}{take pride in}[phrase][B2]
            \EN{To feel satisfaction and pleasure in what you or someone else has achieved.}
            \SY{be proud of; value; appreciate}
            \VI{tự hào về.}
            \EX{She takes pride in her children’s achievements.}
            \EX{The company takes pride in providing good service.}
            \CO{take pride in doing sth; take great pride in sth}
            \end{ExplainCard}
        \end{VocabExplain}

    \noindent
    \textbf{Part 3.}
    \begin{qa}{What are the most difficult jobs that people do?}
    Every job has its own potential threats which may put employees at risk, and it is unjustifiable to choose which one is the most \textbf{arduous}. For example, the role of a firefighter is essentially to protect the lives of the general public during potentially \textbf{life-threatening} situations. Moreover, being a police officer can be very challenging, especially when they have to face \textbf{armed} citizens, who are not \textbf{law-abiding} and can pose dangers to society.
    \end{qa}

    \begin{qa}{Why do you think some people choose to do difficult jobs?}
    There are various reasons why some people are willing to take jobs that are \textbf{inherently} dangerous. For one, these jobs are not as dangerous as they have the most \textbf{rigid} and thorough safety guidelines; thereby reducing the injury and \textbf{fatality rates} that they carry. Besides, a lucrative income is what employees may get from \textbf{these lines of work}, which financially support the employees and their family. \textbf{Procrastination} by making themselves \textbf{accountable} to finish the task.
    \end{qa}

    \begin{qa}{Is it always necessary to work hard in order to achieve career success?}
    Personally, \textbf{toiling night and day} raises people’s chances of success but they cannot rely solely on \textbf{putting in the hours}. \textbf{Working flat out} sometimes pays off, but smart thinking combined with smart work will always help bear fruit in the long run even if people \textbf{stumble} in the short term. Besides, \textbf{working their fingers to the bone} in a long time can make them \textbf{burned out} and lead to serious medical conditions such as depression.
    \end{qa}

    \begin{qa}{Do you think that successful people are always happy people?}
    Achievement can produce the sense of happiness, but this is not true for all cases, I suppose. In other words, people are always under stress to pursue continuous goals, and hardly have time to enjoy the accomplishment that they have achieved. Moreover, unlike \textbf{run-of-the-mill} accomplishments that produce \textbf{fleeting} happiness, the pleasure from \textbf{enduring} accomplishments lasts long after that, which means people will never stop to get new targets.
    \end{qa}
    
        \begin{VocabExplain}[Part 3]
            \begin{ExplainCard}{arduous}[adj][C1]
            \EN{Involving a lot of effort and difficulty.}
            \SY{strenuous; laborious; tough}
            \VI{gian khổ, khó khăn.}
            \EX{Climbing the mountain was an arduous task.}
            \EX{The project proved to be more arduous than expected.}
            \CO{arduous journey; arduous process; arduous task}
            \end{ExplainCard}

            \begin{ExplainCard}{life-threatening}[adj][C1]
            \EN{Very serious; likely to cause death.}
            \SY{fatal; deadly; critical}
            \VI{đe doạ tính mạng.}
            \EX{He is suffering from a life-threatening disease.}
            \EX{Firefighters often work in life-threatening conditions.}
            \CO{life-threatening injury; life-threatening condition}
            \end{ExplainCard}

            \begin{ExplainCard}{armed}[adj][B2]
            \EN{Carrying or using a weapon.}
            \SY{equipped; weaponized}
            \VI{có vũ trang.}
            \EX{The police arrested an armed robber.}
            \EX{Armed guards were standing outside.}
            \CO{armed robbery; armed conflict; armed forces}
            \end{ExplainCard}

            \begin{ExplainCard}{law-abiding}[adj][C1]
            \EN{Obeying and respecting the law.}
            \SY{compliant; obedient}
            \VI{tuân thủ pháp luật.}
            \EX{He is a law-abiding citizen.}
            \EX{Law-abiding people expect protection from the police.}
            \CO{law-abiding citizen; law-abiding behavior}
            \end{ExplainCard}

            \begin{ExplainCard}{inherently}[adv][C1]
            \EN{In a way that is a natural or basic part of something.}
            \SY{intrinsically; essentially}
            \VI{vốn dĩ, cố hữu.}
            \EX{These tasks are inherently difficult.}
            \EX{Human beings are inherently social.}
            \CO{inherently dangerous; inherently flawed}
            \end{ExplainCard}

            \begin{ExplainCard}{rigid}[adj][C1]
            \EN{Very strict and difficult to change.}
            \SY{strict; inflexible}
            \VI{cứng nhắc, nghiêm ngặt.}
            \EX{The school has rigid rules.}
            \EX{Her face set in rigid determination.}
            \CO{rigid structure; rigid guidelines}
            \end{ExplainCard}

            \begin{ExplainCard}{fatality rate}[n][C1]
            \EN{The number of deaths in a particular situation or period.}
            \SY{death rate; mortality rate}
            \VI{tỉ lệ tử vong.}
            \EX{The fatality rate of this disease is quite high.}
            \EX{Car accidents still show high fatality rates.}
            \CO{high fatality rate; reduce fatality rate}
            \end{ExplainCard}

            \begin{ExplainCard}{line of work}[phrase][B2]
            \EN{The type of work someone does.}
            \SY{occupation; profession; trade}
            \VI{nghề nghiệp, lĩnh vực công việc.}
            \EX{He chose medicine as his line of work.}
            \EX{This line of work requires dedication.}
            \CO{in this line of work; dangerous line of work}
            \end{ExplainCard}

            \begin{ExplainCard}{accountable}[adj][C1]
            \EN{Responsible for what you do and able to explain actions.}
            \SY{responsible; liable; answerable}
            \VI{chịu trách nhiệm.}
            \EX{Managers are accountable for their decisions.}
            \EX{He is accountable to the board of directors.}
            \CO{hold sb accountable; accountable for sth}
            \end{ExplainCard}

            \begin{ExplainCard}{toil night and day}[idiom][C1]
            \EN{To work very hard for a long time.}
            \SY{slave away; grind}
            \VI{làm việc ngày đêm.}
            \EX{She toiled night and day to finish the project.}
            \EX{They toiled night and day for their family’s future.}
            \CO{toil night and day at sth}
            \end{ExplainCard}

            \begin{ExplainCard}{put in the hours}[idiom][C1]
            \EN{To spend a lot of time working.}
            \SY{work long hours; devote time}
            \VI{dành nhiều giờ làm việc.}
            \EX{You’ll succeed if you put in the hours.}
            \EX{He put in the hours to master the skill.}
            \CO{put in the hours at work/study}
            \end{ExplainCard}

            \begin{ExplainCard}{work flat out}[idiom][C1]
            \EN{To work very hard without stopping.}
            \SY{work nonstop; work tirelessly}
            \VI{làm việc hết công suất.}
            \EX{They worked flat out to meet the deadline.}
            \EX{She worked flat out to complete her essay.}
            \CO{work flat out to do sth}
            \end{ExplainCard}

            \begin{ExplainCard}{stumble}[v][C1]
            \EN{To make mistakes or experience difficulties.}
            \SY{struggle; falter; trip}
            \VI{vấp ngã, gặp khó khăn.}
            \EX{He stumbled over his words.}
            \EX{The project stumbled in its early stages.}
            \CO{stumble over sth; stumble in sth}
            \end{ExplainCard}

            \begin{ExplainCard}{work one’s fingers to the bone}[idiom][C1]
            \EN{To work extremely hard, often to the point of exhaustion.}
            \SY{overwork; exhaust oneself}
            \VI{làm việc đến kiệt sức.}
            \EX{She worked her fingers to the bone for her family.}
            \EX{They worked their fingers to the bone to build the business.}
            \CO{work one’s fingers to the bone for sth}
            \end{ExplainCard}

            \begin{ExplainCard}{burned out}[adj][C1]
            \EN{Physically or mentally exhausted due to overwork.}
            \SY{exhausted; fatigued}
            \VI{kiệt sức, cháy sạch năng lượng.}
            \EX{He got burned out after years in a stressful job.}
            \EX{Teachers often feel burned out mid-semester.}
            \CO{feel burned out; become burned out}
            \end{ExplainCard}

            \begin{ExplainCard}{run-of-the-mill}[adj][C1]
            \EN{Ordinary and not special.}
            \SY{average; common; mundane}
            \VI{bình thường, tầm thường.}
            \EX{It was just a run-of-the-mill performance.}
            \EX{He lives a run-of-the-mill life.}
            \CO{run-of-the-mill job; run-of-the-mill event}
            \end{ExplainCard}

            \begin{ExplainCard}{fleeting}[adj][C1]
            \EN{Lasting for only a short time.}
            \SY{brief; short-lived; passing}
            \VI{thoáng qua, ngắn ngủi.}
            \EX{She had a fleeting smile.}
            \EX{It was a fleeting moment of happiness.}
            \CO{fleeting moment; fleeting glance}
            \end{ExplainCard}

            \begin{ExplainCard}{enduring}[adj][C1]
            \EN{Lasting for a long time.}
            \SY{lasting; long-term; permanent}
            \VI{lâu dài, bền bỉ.}
            \EX{She left an enduring legacy.}
            \EX{Their enduring friendship is admirable.}
            \CO{enduring memory; enduring success; enduring appeal}
            \end{ExplainCard}
        \end{VocabExplain}

        \begin{VocabHighlights}
            \VH{as busy as a bee}{(idiom) very busy}{(thành ngữ) rất bận rộn}
            \VH{to have a lie-in}{(idiom) to oversleep}{(thành ngữ) ngủ nướng}
            \VH{I don't have the vaguest idea}{(phrase) I don't know anything about}{(cụm từ) tôi không biết tí gì về}
            \VH{to stick one's nose in other's business}{(idiom) to interfere in one's business}{(thành ngữ) can thiệp vào việc người khác}
            \VH{to make up stories}{(phr.v) to invent stories}{(cụm động từ) bịa chuyện}
            \VH{to get down to V-ing}{(phr.v) to start doing something seriously}{(cụm động từ) làm gì nghiêm túc}
            \VH{in an instant}{(idiom) instantly}{(thành ngữ) ngay lập tức}
            \VH{in all sincerity}{(idiom) truth be told}{(thành ngữ) thực ra mà nói thì}
            \VH{more or less}{(phrase) approximately}{(cụm từ) ít nhiều, xấp xỉ}
            \VH{to present a challenge}{(phrase) create a difficult task}{(cụm từ) tạo ra thách thức}
            \VH{to make heads or tails of}{(idiom) understand something}{(thành ngữ) hiểu}
            \VH{to struggle to V-inf}{(v) to spend much time overcoming something}{(động từ) vật lộn, chật vật}
            \VH{to come up with}{(phr.v) think of a new idea}{(cụm động từ) nảy ra ý kiến}
            \VH{beyond somebody's ken}{(idiom) not in one's area of knowledge}{(thành ngữ) vẫn không thể hiểu}
            \VH{to accumulate}{(v) gather something}{(động từ) tích lũy}
            \VH{to let somebody down}{(phr.v) make somebody disappointed}{(cụm động từ) làm ai đó thất vọng}
            \VH{to burst into tears}{(phrase) be moved to tears}{(cụm từ) cảm động đến rơi nước mắt}
            \VH{on cloud nine}{(idiom) be happy}{(thành ngữ) hạnh phúc, sung sướng}
            \VH{to take pride in}{(phrase) to be proud of}{(cụm từ) tự hào về}
            \VH{arduous}{(adj) involving a lot of effort and energy, especially over a period of time}{(tính từ) gian truân}
            \VH{life-threatening}{(adj) able to cause death}{(tính từ) gây nguy hiểm}
            \VH{armed}{(adj) equipped with or carrying a weapon or weapons}{(tính từ) có vũ khí}
            \VH{law-abiding}{(adj) obedient to the laws of society}{(tính từ) tuân thủ luật pháp}
            \VH{inherently}{(adv) according to or because of the basic nature of somebody/something}{(trạng từ) về bản chất}
            \VH{rigid}{(adj) very strict and difficult to change}{(tính từ) nghiêm ngặt}
            \VH{fatality rate}{(phrase) death rate}{(cụm từ) tỉ lệ tử vong}
            \VH{these lines of work}{(phrase) an occupation}{(cụm từ) ngành nghề}
            \VH{at their wits' end}{(idiom) feel very upset}{(thành ngữ) buồn chán}
            \VH{fierce competition}{(phrase) a very determined competition}{(cụm từ) cạnh tranh khốc liệt}
            \VH{pull an all-nighter}{(idiom) a time when you spend all night working}{(thành ngữ) làm cú đêm}
            \VH{attainable}{(adj) that you can achieve}{(tính từ) có thể đạt được}
            \VH{benchmark}{(n) something that can be measured and used as a standard that other things can be compared with}{(danh từ) tiêu chuẩn}
            \VH{procrastination}{(n) the act of delaying something that you should do, usually because you do not want to do it}{(danh từ) sự trì hoãn}
            \VH{accountable}{(adj) responsible for your decisions or actions and expected to explain them when you are asked}{(tính từ) chịu trách nhiệm}
            \VH{to toil night and day}{(phrase) to work hard all day}{(cụm từ) làm việc quần quật cả ngày}
            \VH{put in the hours}{(phrase) to work overtime}{(cụm từ) làm việc quá giờ}
            \VH{to work flat out}{(idiom) work very hard}{(thành ngữ) làm việc chăm chỉ}
            \VH{to stumble}{(v) a problem or temporary failure when you are on the way to achieving something}{(động từ) vấp phải}
            \VH{to work one's fingers to the bone}{(idiom) to work extremely hard, especially for a long time}{(thành ngữ) làm việc cực kì chăm chỉ lâu dài}
            \VH{burned out}{(adj) exhausted}{(tính từ) kiệt sức}
            \VH{run-of-the-mill}{(phrase) lacking unusual or special aspects; ordinary}{(cụm từ) thiếu sáng tạo}
            \VH{fleeting}{(adj) short or quick}{(tính từ) thoáng qua}
            \VH{enduring}{(adj) existing for a long time}{(tính từ) kéo dài}
        \end{VocabHighlights}
    \end{test}

    \begin{test}{TEST 4}
    \noindent
    \textbf{Part 1. Neighbours}
    \begin{qa}{Do you like the neighbourhood you live in? [Why/Why not?]}
    Yes, I do. Although I’m not in the habit of interacting with others, I still treasure every moment of living here. As long as my reputation hasn’t been ruined and I haven’t heard any untrue stories about me, I still wish to \textbf{linger here} as long as possible.
    \end{qa}

    \begin{qa}{What do you do in your neighbourhood in your free time? [Why/Why not?]}
    The thing I frequently do in my spare time in my neighborhood \textbf{revolves around} shopping at some convenience stores on the first floor. However small they are, they still offer a variety of products that may \textbf{come in handy} for my house so I’ve \textbf{taken up} the hobby of shopping at these stores when I’m off work.
    \end{qa}

    \begin{qa}{What new things would you like to have in your neighbourhood? [Why/Why not?]}
    There are two things which I believe should come into existence in my neighborhood. Firstly, a new parking lot, \textbf{preferably} underground, should become a reality. The currently overground car park is often \textbf{packed like sardines}, making it inconvenient for me to park mine. Secondly, I would like the hall room on the ground floor to have a big screen TV installed so in the event of an important football \textbf{match}, everyone can gather in front of the TV and support their favorite teams together. It’s a good way for people to get to know each other, too.
    \end{qa}

    \begin{qa}{Would you like to live in another neighbourhood in your town or city? [Why/Why not?]}
    No one can predict the future. As far as I’m concerned, I still live \textbf{in harmony with} everyone, not to mention that the distance from where I live to the workplace is just a \textbf{stone’s throw}. I don’t \textbf{feel the urge} to move to anywhere else. Remaining here is still my priority now.
    \end{qa}

        \begin{VocabExplain}[Part 1]
            \begin{ExplainCard}{linger}[v][C1]
            \EN{To stay somewhere longer than expected or necessary.}
            \SY{remain; stay; persist}
            \VI{nán lại, kéo dài.}
            \EX{She lingered outside after the meeting.}
            \EX{The smell of smoke lingered in the room.}
            \CO{linger on; linger over sth; linger here}
            \end{ExplainCard}

            \begin{ExplainCard}{revolve around}[phr.v][B2]
            \EN{To have something as the main subject or focus.}
            \SY{center on; focus on}
            \VI{xoay quanh.}
            \EX{Her life revolves around her children.}
            \EX{The discussion revolved around climate change.}
            \CO{revolve around sth}
            \end{ExplainCard}

            \begin{ExplainCard}{come in handy}[idiom][B2]
            \EN{To be useful in a particular situation.}
            \SY{be useful; be of use}
            \VI{hữu ích.}
            \EX{This dictionary will come in handy for your studies.}
            \EX{The flashlight came in handy during the blackout.}
            \CO{come in handy for sth}
            \end{ExplainCard}

            \begin{ExplainCard}{take up}[phr.v][B2]
            \EN{To start a new hobby or activity.}
            \SY{begin; start; engage in}
            \VI{bắt đầu làm gì.}
            \EX{He took up swimming last year.}
            \EX{She has recently taken up painting.}
            \CO{take up a hobby; take up a sport}
            \end{ExplainCard}

            \begin{ExplainCard}{preferably}[adv][B2]
            \EN{Used to show that one choice is more suitable than others.}
            \SY{ideally; desirably}
            \VI{tốt nhất là, lý tưởng nhất là.}
            \EX{Arrive early, preferably before 9 a.m.}
            \EX{She wants to live in the city, preferably downtown.}
            \CO{preferably with/without sth}
            \end{ExplainCard}

            \begin{ExplainCard}{packed like sardines}[idiom][C1]
            \EN{Very crowded, with people pressed closely together.}
            \SY{overcrowded; jam-packed}
            \VI{đông nghẹt, chen chúc.}
            \EX{We were packed like sardines on the bus.}
            \EX{The stadium was packed like sardines.}
            \CO{be packed like sardines in sth}
            \end{ExplainCard}

            \begin{ExplainCard}{match}[n][B1]
            \EN{A sports competition between two people or teams.}
            \SY{game; contest}
            \VI{trận đấu.}
            \EX{They played a football match yesterday.}
            \EX{The match ended in a draw.}
            \CO{football match; tennis match}
            \end{ExplainCard}

            \begin{ExplainCard}{in harmony with}[phrase][C1]
            \EN{To live or work peacefully together.}
            \SY{in agreement; in unity}
            \VI{sống hoà hợp với.}
            \EX{She lives in harmony with nature.}
            \EX{They tried to live in harmony with their neighbors.}
            \CO{live/work in harmony with sb/sth}
            \end{ExplainCard}

            \begin{ExplainCard}{a stone’s throw}[idiom][C1]
            \EN{A very short distance.}
            \SY{near; close by}
            \VI{rất gần, cách một quãng ngắn.}
            \EX{The school is just a stone’s throw from here.}
            \EX{The hotel is only a stone’s throw from the beach.}
            \CO{a stone’s throw away from sth}
            \end{ExplainCard}

            \begin{ExplainCard}{feel the urge}[phrase][C1]
            \EN{To strongly want to do something.}
            \SY{desire; long for; crave}
            \VI{cảm thấy thôi thúc.}
            \EX{She felt the urge to cry.}
            \EX{He felt the urge to travel abroad.}
            \CO{feel the urge to do sth}
            \end{ExplainCard}
        \end{VocabExplain}

    \noindent
    \textbf{Part 2.}
    \begin{qa}{Describe a website you have bought something from. You should say:}
    \begin{itemize}
        \item What the website is  
        \item What you bought from this website  
        \item How satisfied you were with what you bought  
        \item and explain what you liked and disliked about using this website.  
    \end{itemize}

    To be honest, I am a shopaholic, so I \textbf{have a habit of} online shopping in my leisure time. A website that is gaining in popularity in Vietnam is Shopee. To the best of my knowledge, it \textbf{keeps the lion share} of e-commerce market in Vietnam \textbf{to date}. I \textbf{stumbled on} this website one year ago while surfing the Internet on my smartphone. At that time, I was going to \textbf{shop for} a new hairdryer to replace the old one that was \textbf{out of order}. I searched for information about brands or new features on the Internet.  

    The advertisements from this website caught my attention since there was a big \textbf{promotional campaign}. Some brands cut prices, so I did not have to \textbf{pay full price}. Without hesitation, I ordered one product on the website. To be honest, I \textbf{felt on top of the world} because it was a \textbf{real bargain}.  

    A reason why I was into using this website is that it was \textbf{user-friendly}, so familiarizing myself with its interface was not \textbf{over my head}. More importantly, I could compare the prices among brands in \textbf{different outlets}, so I can easily find the best deals. If you ask me what aspect of this website I \textbf{was not content with}, I think that there was limited room for reviews, but I guess it was not much of a problem.
    \end{qa}

        \begin{VocabExplain}[Part 2]
            \begin{ExplainCard}{have a habit of}[phrase][B2]
            \EN{To do something regularly or repeatedly, often without thinking.}
            \SY{be accustomed to; be prone to}
            \VI{có thói quen làm gì.}
            \EX{She has a habit of checking her phone every few minutes.}
            \EX{I have a habit of drinking coffee late at night.}
            \CO{have a habit of doing sth}
            \end{ExplainCard}

            \begin{ExplainCard}{keep the lion share}[idiom][C1]
            \EN{To hold or take the largest part of something.}
            \SY{dominate; take the majority}
            \VI{chiếm phần lớn.}
            \EX{This company keeps the lion’s share of the smartphone market.}
            \EX{He always tries to keep the lion’s share of the profits.}
            \CO{lion’s share of sth}
            \end{ExplainCard}

            \begin{ExplainCard}{to date}[phrase][B2]
            \EN{Until now; up to the present time.}
            \SY{so far; up to now}
            \VI{cho đến nay.}
            \EX{This is her best book to date.}
            \EX{The project has cost \$5 million to date.}
            \CO{best/worst/largest to date}
            \end{ExplainCard}

            \begin{ExplainCard}{stumble on}[phr.v][C1]
            \EN{To discover something by chance.}
            \SY{come across; run into}
            \VI{tình cờ phát hiện.}
            \EX{I stumbled on an old photo album in the attic.}
            \EX{They stumbled on a great little restaurant.}
            \CO{stumble on/upon sth}
            \end{ExplainCard}

            \begin{ExplainCard}{out of order}[phrase][B1]
            \EN{Not working properly.}
            \SY{broken; defective}
            \VI{hỏng hóc.}
            \EX{The vending machine is out of order.}
            \EX{Her laptop was out of order for a week.}
            \CO{be out of order}
            \end{ExplainCard}

            \begin{ExplainCard}{promotional campaign}[n][B2]
            \EN{A planned series of activities to promote a product or service.}
            \SY{advertising campaign; marketing drive}
            \VI{chiến dịch quảng bá.}
            \EX{The company launched a new promotional campaign for its product.}
            \EX{Promotional campaigns often increase sales significantly.}
            \CO{launch/run a promotional campaign}
            \end{ExplainCard}

            \begin{ExplainCard}{pay full price}[phrase][B2]
            \EN{To pay the complete price without discount.}
            \SY{pay in full; pay the standard rate}
            \VI{trả đủ giá, không giảm giá.}
            \EX{I bought the shoes on sale, so I didn’t have to pay full price.}
            \EX{Some customers are willing to pay full price for quality goods.}
            \CO{pay full price for sth}
            \end{ExplainCard}

            \begin{ExplainCard}{on top of the world}[idiom][C1]
            \EN{Feeling extremely happy.}
            \SY{overjoyed; ecstatic}
            \VI{vui sướng tột cùng.}
            \EX{She felt on top of the world after passing the exam.}
            \EX{Winning the prize made him feel on top of the world.}
            \CO{feel on top of the world}
            \end{ExplainCard}

            \begin{ExplainCard}{real bargain}[n][B2]
            \EN{Something bought cheaply and worth more than paid.}
            \SY{good deal; steal}
            \VI{món hời.}
            \EX{I got this coat for \$20 – it was a real bargain.}
            \EX{That car is a real bargain for the price.}
            \CO{get/find a real bargain}
            \end{ExplainCard}

            \begin{ExplainCard}{user-friendly}[adj][B2]
            \EN{Easy for people to use.}
            \SY{intuitive; simple}
            \VI{dễ sử dụng.}
            \EX{The new software is very user-friendly.}
            \EX{We need a more user-friendly website.}
            \CO{user-friendly design; user-friendly system}
            \end{ExplainCard}

            \begin{ExplainCard}{over my head}[idiom][C1]
            \EN{Too difficult to understand.}
            \SY{beyond comprehension; too complex}
            \VI{vượt ngoài tầm hiểu biết.}
            \EX{The lecture was completely over my head.}
            \EX{These instructions are a bit over my head.}
            \CO{go over sb’s head}
            \end{ExplainCard}

            \begin{ExplainCard}{outlet}[n][B2]
            \EN{A shop that sells goods of a particular brand, often at reduced prices.}
            \SY{store; branch}
            \VI{cửa hàng, đại lý.}
            \EX{I bought these shoes at a Nike outlet.}
            \EX{Factory outlets sell products at discount.}
            \CO{outlet store; retail outlet}
            \end{ExplainCard}

            \begin{ExplainCard}{content with}[phrase][C1]
            \EN{Satisfied with what one has or experiences.}
            \SY{satisfied; pleased}
            \VI{hài lòng với.}
            \EX{She was content with her simple life.}
            \EX{He felt content with the results of his work.}
            \CO{be content with sth}
            \end{ExplainCard}
        \end{VocabExplain}

    \noindent
    \textbf{Part 3.}
    \begin{qa}{What kinds of things do people in your country often buy from online shops?}
    As far as I know, there are many things that customers could consider buying from virtual shops. Books are one of the first products that are widely sold online so potential buyers do not need to physically \textbf{dip into} a book before buying it. Sites like Tiki, newshop.vn, etc. now offer \textbf{sneak-preview} features that let website visitors \textbf{peek at} the contents before deciding whether to buy or not. Luggage is another good item to buy online as it is bulky, and buying online saves users the trouble of \textbf{hauling} it home from the store.
    \end{qa}

    \begin{qa}{Why has online shopping become so popular in many countries?}
    Understandably, shopping online is regarded as a \textbf{shopping therapy} for many reasons. Online shopping provides customers the facility to \textbf{shop till they drop}, which means they do not have to depend on someone or take off some extra time for shopping. More importantly, there are offers and discounts available on online websites, and the customers can easily pick up a \textbf{bargain}.
    \end{qa}

    \begin{qa}{What are some possible disadvantages of buying things from online shops?}
    Well, online \textbf{fraudulence} is radically \textbf{a far cry from} ones typically seen in brick-and-mortar businesses. There will always be \textbf{unscrupulous} people whose only goal is to either \textbf{rip off} your business or get something for nothing. One of the most common frauds when customers go shopping online is identity theft which a \textbf{fraudster} carries out by using someone else’s credit card. This can cause huge financial loss to the users.
    \end{qa}

    \begin{qa}{Do you agree that the prices of all goods should be lower on internet shopping sites than in shops?}
    Personally, I agree the prices of online products should be lower than physical ones. This is because retailers do not always offer the same deals in brick-and-mortar stores as at their online counterparts because the cost of running a physical establishment can be considerably greater. Retailers can meet the needs of their customers with less operational expense, then help the customers to \textbf{save a bundle} by cutting the cost. However, this is not the case for \textbf{liquidated goods} which may be sold below the \textbf{wholesale price} in both physical and online stores.
    \end{qa}

    \begin{qa}{Will large shopping malls continue to be popular despite the growth of internet shopping?}
    To be honest, the \textbf{outlook} on the development of online shopping and in-store shopping might be unpredictable. To many \textbf{onlookers}, the wave looks like it may send brick-and-mortar shops \textbf{into a tailspin} because with the help of the Internet, brand owners could know the exact needs, sizes and preferences and automatically provide the products that customers need. However, it is expected that real-life stores will still hold out as luxurious items such as cars or jewellery cannot be sold online.
    \end{qa}

    \begin{qa}{Do you think that some businesses (e.g. banks and travel agents) will only operate online in the future?}
    Well, in the case of some businesses such as banks or travel agents going online, there is a whole range of security threats such as malware or phishing attacks. These threats could \textbf{steal off} the money of customers in a \textbf{fraction of a second} once the online system is hacked. That is why physical banks or travel agents should not be totally replaced by the online system.
    \end{qa}

        \begin{VocabExplain}[Part 3]
            \begin{ExplainCard}{dip into}[phr.v][C1]
            \EN{To read, watch, or use only a small part of something, not all of it.}
            \SY{skim; glance through}
            \VI{xem lướt qua, dùng qua một phần nhỏ.}
            \EX{She dipped into the book before deciding to buy it.}
            \EX{He often dips into his savings to cover small expenses.}
            \CO{dip into a book; dip into savings}
            \end{ExplainCard}

            \begin{ExplainCard}{sneak-preview}[n][C1]
            \EN{An early opportunity to see, hear, or experience something before it becomes widely available.}
            \SY{preview; teaser}
            \VI{cái nhìn trước, bản xem thử.}
            \EX{The magazine offered a sneak-preview of next month’s issue.}
            \EX{Fans got a sneak-preview of the new movie.}
            \CO{sneak-preview version; sneak-preview feature}
            \end{ExplainCard}

            \begin{ExplainCard}{peek at}[phr.v][B2]
            \EN{To look quickly at something, often secretly or briefly.}
            \SY{glance; glimpse}
            \VI{nhìn trộm, nhìn thoáng qua.}
            \EX{She peeked at the answers on the exam sheet.}
            \EX{He peeked at the document before signing.}
            \CO{peek at notes; peek at contents}
            \end{ExplainCard}

            \begin{ExplainCard}{haul}[v][B2]
            \EN{To pull or transport something heavy with effort.}
            \SY{drag; lug; carry}
            \VI{kéo, vận chuyển vật nặng.}
            \EX{Fishermen hauled their nets onto the boat.}
            \EX{She had to haul her luggage across the station.}
            \CO{haul goods; haul equipment; haul cargo}
            \end{ExplainCard}

            \begin{ExplainCard}{shopping therapy}[n][C1]
            \EN{The practice of shopping to relieve stress or improve one’s mood.}
            \SY{retail therapy}
            \VI{mua sắm như liệu pháp tinh thần.}
            \EX{Many people rely on shopping therapy after a bad day.}
            \EX{Shopping therapy gives her temporary relief from stress.}
            \CO{do shopping therapy; indulge in shopping therapy}
            \end{ExplainCard}

            \begin{ExplainCard}{shop till you drop}[idiom][B2]
            \EN{To shop for a very long time until you are extremely tired.}
            \SY{shop endlessly; spree shop}
            \VI{mua sắm đến kiệt sức.}
            \EX{They shopped till they dropped at the holiday sales.}
            \EX{During Black Friday, customers shop till they drop.}
            \CO{shop till you drop}
            \end{ExplainCard}

            \begin{ExplainCard}{fraudulence}[n][C1]
            \EN{The state of being deceptive, dishonest, or involving crime for personal gain.}
            \SY{dishonesty; scam; deception}
            \VI{sự gian lận.}
            \EX{The fraudulence of the scheme shocked investors.}
            \EX{Online fraudulence is becoming more sophisticated.}
            \CO{online fraudulence; financial fraudulence}
            \end{ExplainCard}

            \begin{ExplainCard}{a far cry from}[idiom][C1]
            \EN{Completely different from something else.}
            \SY{totally different; unlike}
            \VI{khác xa với.}
            \EX{The service was a far cry from what we expected.}
            \EX{His new book is a far cry from his previous works.}
            \CO{a far cry from reality; a far cry from expectations}
            \end{ExplainCard}

            \begin{ExplainCard}{unscrupulous}[adj][C1]
            \EN{Without moral principles; dishonest or unfair.}
            \SY{dishonest; unethical; corrupt}
            \VI{vô lương tâm, phi đạo đức.}
            \EX{Unscrupulous dealers cheat customers easily.}
            \EX{The market is full of unscrupulous middlemen.}
            \CO{unscrupulous traders; unscrupulous practices}
            \end{ExplainCard}

            \begin{ExplainCard}{rip off}[phr.v][C1]
            \EN{To cheat someone, especially by charging them too much.}
            \SY{overcharge; swindle; exploit}
            \VI{chặt chém, lừa đảo.}
            \EX{Tourists were ripped off at the local market.}
            \EX{The taxi driver ripped me off by doubling the fare.}
            \CO{rip sb off; a rip-off deal}
            \end{ExplainCard}

            \begin{ExplainCard}{fraudster}[n][C1]
            \EN{A person who commits fraud, especially to gain money illegally.}
            \SY{swindler; scammer; deceiver}
            \VI{kẻ lừa đảo.}
            \EX{The fraudster used stolen cards to shop online.}
            \EX{Police arrested a notorious fraudster yesterday.}
            \CO{catch a fraudster; online fraudster}
            \end{ExplainCard}

            \begin{ExplainCard}{save a bundle}[idiom][C1]
            \EN{To save a large amount of money.}
            \SY{save a fortune; economize}
            \VI{tiết kiệm được rất nhiều tiền.}
            \EX{Buying in bulk saves a bundle.}
            \EX{She saved a bundle by booking flights early.}
            \CO{save a bundle on sth}
            \end{ExplainCard}

            \begin{ExplainCard}{liquidated goods}[n][C1]
            \EN{Products sold quickly at reduced prices, often to clear stock.}
            \SY{clearance items; discounted stock}
            \VI{hàng thanh lý.}
            \EX{They sold liquidated goods after the store closed.}
            \EX{Liquidated goods are usually cheaper than wholesale.}
            \CO{liquidated goods sale; buy liquidated goods}
            \end{ExplainCard}

            \begin{ExplainCard}{wholesale price}[n][B2]
            \EN{The price charged for goods when sold in large quantities to stores or distributors.}
            \SY{bulk price}
            \VI{giá bán sỉ.}
            \EX{Shops buy at wholesale prices to resell.}
            \EX{The wholesale price is much cheaper than retail.}
            \CO{wholesale price list; wholesale price increase}
            \end{ExplainCard}

            \begin{ExplainCard}{outlook}[n][B2]
            \EN{The likely future situation, perspective, or attitude.}
            \SY{prospect; forecast; expectation}
            \VI{triển vọng, quan điểm.}
            \EX{The economic outlook is optimistic.}
            \EX{He has a broad outlook on life.}
            \CO{economic outlook; outlook on sth}
            \end{ExplainCard}

            \begin{ExplainCard}{onlookers}[n][B2]
            \EN{People who watch an event happen without participating.}
            \SY{spectators; witnesses}
            \VI{người đứng xem.}
            \EX{Onlookers gathered at the accident scene.}
            \EX{The show attracted many curious onlookers.}
            \CO{curious onlookers; attract onlookers}
            \end{ExplainCard}

            \begin{ExplainCard}{into a tailspin}[idiom][C1]
            \EN{A state of uncontrolled decline, confusion, or chaos.}
            \SY{turmoil; collapse; downfall}
            \VI{rơi vào khủng hoảng, hỗn loạn.}
            \EX{The scandal sent the company into a tailspin.}
            \EX{Markets went into a tailspin after the announcement.}
            \CO{fall/go into a tailspin}
            \end{ExplainCard}

            \begin{ExplainCard}{steal off}[phr.v][C1]
            \EN{To move or take something secretly and quickly.}
            \SY{snatch; sneak away}
            \VI{ăn cắp, lặng lẽ bỏ đi.}
            \EX{He stole off with her purse in the crowd.}
            \EX{Hackers could steal off funds online.}
            \CO{steal off with sth}
            \end{ExplainCard}

            \begin{ExplainCard}{fraction of a second}[phrase][B2]
            \EN{A very short time, almost instant.}
            \SY{split second; blink of an eye}
            \VI{trong tích tắc, chớp mắt.}
            \EX{The car disappeared in a fraction of a second.}
            \EX{He reacted in a fraction of a second.}
            \CO{in a fraction of a second}
            \end{ExplainCard}
        \end{VocabExplain}

    \begin{VocabHighlights}
        \VH{to linger}{(v) to stay somewhere for longer because you do not want to leave; to spend a long time doing something}{(động từ) muốn ở lâu nơi đâu}
        \VH{to revolve around}{(phr.v) to have somebody/something as the main interest or subject}{(cụm động từ) xoay quanh}
        \VH{to come in handy}{(adj) to be useful}{(tính từ) hữu dụng}
        \VH{to take up}{(phr.v) to learn or start to do something, especially for pleasure}{(cụm động từ) học làm gì (giải trí, sở thích)}
        \VH{preferably}{(adv) in a way that is more attractive or more suitable; in a way that is preferred to other ways}{(trạng từ) thích hơn là}
        \VH{to be packed like sardines}{(idiom) to be very crowded}{(thành ngữ) rất đông đúc}
        \VH{in harmony with}{(idiom) in a state of peaceful existence and agreement}{(thành ngữ) hòa hợp cùng với}
        \VH{a stone's throw}{(idiom) very close}{(thành ngữ) rất gần}
        \VH{to feel the urge}{(phrase) to feel it's necessary to V-inf}{(cụm từ) cảm thấy cần làm gì}
        \VH{all the rage}{(idiom) be popular}{(thành ngữ) đang nổi tiếng}
        \VH{to keep the lion's share of}{(idiom) hold the largest proportion of something}{(thành ngữ) chiếm phần lớn thị phần}
        \VH{to date}{(phrase) until now}{(cụm từ) cho tới bây giờ}
        \VH{to stumble on}{(phrase) find something unexpectedly}{(cụm từ) phát hiện tình cờ}
        \VH{promotional campaign}{(phrase) a program aimed to boost sales}{(cụm từ) chiến dịch xúc tiến}
        \VH{out of order}{(idiom) to fail to function properly}{(thành ngữ) hỏng}
        \VH{to pay full price}{(phrase) pay full price}{(cụm từ) trả giá đúng, như mắc}
        \VH{to be on top of the world}{(idiom) happy and elated}{(thành ngữ) vui sướng}
        \VH{a real bargain}{(phrase) something that saves buyers money}{(cụm từ) món hời}
        \VH{user-friendly}{(adj) easy to use}{(tính từ) dễ sử dụng}
        \VH{over my head}{(idiom) too difficult or strange to understand}{(thành ngữ) quá khó để hiểu}
        \VH{outlets}{(n) a shop that sells something (at a reduced price)}{(danh từ) cửa hàng bán đồ giảm giá}
        \VH{to be content with}{(phrase) be happy with something}{(cụm từ) hài lòng với}
        \VH{to dip into}{(phr.v) to read, watch, or listen to small amounts of something}{(cụm động từ) đọc lướt qua}
        \VH{sneak-preview}{(n) an opportunity to see something before it is officially shown}{(danh từ) xem trước}
        \VH{to peek}{(v) a quick and secret look at something}{(động từ) nhìn lướt}
        \VH{to haul}{(v) to pull something/somebody with a lot of effort}{(động từ) vận chuyển}
        \VH{shopping therapy}{(phrase) shopping to improve mood or disposition}{(cụm từ) liệu pháp mua sắm}
        \VH{to shop till somebody drop(s)}{(idiom) to do a large amount of shopping}{(thành ngữ) mua sắm nhiều}
        \VH{a bargain}{(n) a thing sold more cheaply than usual}{(danh từ) sự mặc cả}
        \VH{fraudulence}{(n) dishonest and illegal deception}{(danh từ) lừa đảo}
        \VH{a far cry from}{(phrase) very different from}{(cụm từ) rất khác với}
        \VH{unscrupulous}{(adj) without moral principles}{(tính từ) vô đạo đức}
        \VH{to rip off}{(phr.v) to cheat somebody by overcharging or selling poor quality}{(cụm động từ) lừa mua hàng giá cao}
        \VH{a fraudster}{(n) a person who commits fraud}{(danh từ) kẻ lừa đảo}
        \VH{online counterparts}{(n) a person or thing that has the same purpose as another one in a different place or organization}{(danh từ) đồng nghiệp, bạn trực tuyến}
        \VH{to save a bundle}{(phrase) save a lot}{(cụm từ) tiết kiệm được nhiều}
        \VH{liquidated goods}{(n) old things}{(danh từ) hàng thanh lý}
        \VH{wholesale price}{(n) the price charged for a product as sold in bulk to large trade}{(danh từ) giá bán buôn}
        \VH{outlook}{(n) the attitude to life and the world of a particular person, group or culture}{(danh từ) triển vọng}
        \VH{onlookers}{(n) a person who watches something that is happening but is not involved in it}{(danh từ) người ngoài cuộc}
        \VH{into a tailspin}{(idiom) a situation that suddenly becomes much worse and is not under control}{(thành ngữ) mất kiểm soát}
        \VH{malware}{(n) software such as a virus on a computer or computer network that the user does not know about or want}{(danh từ) phần mềm độc hại}
        \VH{to steal off}{(phr.v) to take (money or property) illegally or without consent}{(cụm động từ) lấy trộm}
        \VH{a fraction of a second}{(phrase) a tiny amount or proportion of time}{(cụm từ) trong tích tắc}
    \end{VocabHighlights}
    \end{test}
\end{glossarymc}